---
title: "2018 Annual heat emission from EnergyPlus simulation finer grid"
author: "Yujie Xu"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning=FALSE)
knitr::opts_knit$set(root.dir = "~/Dropbox/workLBNL/EESA/code/im3-wrf/")
```

```{r helpers, message=FALSE}
library("dplyr")
library("tmap")

get.spatial.path.suf <- function(spatial.level) {
  if (spatial.level == "coarse") {
    spatial.path = "M02_EnergyPlus_Forcing_Historical_LowRes/meta"
    spatial.suf = ""
    spatial.label = "Coarse Grids"
  } else if (spatial.level == "finer") {
    spatial.path = "high res grid for reporting"
    spatial.suf = "_finer"
    spatial.label = "Finer Grids"
  } else if (spatial.level == "tract") {
    spatial.path = "domain/tl_2018_06_tract"
    ## spatial.path = "domain"
    spatial.suf = "_tract"
    spatial.label = "Census Tract"
  }
  list(spatial.path, spatial.suf, spatial.label)
}

get.annual.data <- function(time.pref, spatial.suf, df.area=NULL) {
  heat.by.grid.monthly = readr::read_csv(sprintf("aggregated_heat/%s%s_monthly.csv", time.pref, spatial.suf))
  heat.by.grid.annual.comp = heat.by.grid.monthly %>%
    dplyr::group_by(id, variable) %>%
    dplyr::summarise(value = sum(value)) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(emission.GJ = value * 1e-9) %>%
    dplyr::mutate(emission.mwh = emission.GJ * 0.277778) %>%
    {.}
  if (!is.null(df.area)) {
    heat.by.grid.annual.comp <- heat.by.grid.annual.comp %>%
      dplyr::left_join(df.area, by="id") %>%
      dplyr::mutate(emission.wperm2 = value * 0.000277778 / 8760 / area.m2) %>%
      {.}
  }
  heat.by.grid.annual.comp
}

get.monthly.data <- function(time.pref, spatial.suf, df.area=NULL) {
  heat.by.grid.monthly = readr::read_csv(sprintf("aggregated_heat/%s%s_monthly.csv", time.pref, spatial.suf))
  heat.by.grid.monthly.comp = heat.by.grid.monthly %>%
    dplyr::mutate(emission.GJ = value * 1e-9) %>%
    dplyr::mutate(emission.mwh = emission.GJ * 0.277778) %>%
    {.}
  if (!is.null(df.area)) {
    hours.in.month = tibble::tibble(month=sprintf("%02d", 1:12), hours=c(31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31) * 24)
    heat.by.grid.monthly.comp <- heat.by.grid.monthly.comp %>%
      dplyr::left_join(df.area, by="id") %>%
      dplyr::left_join(hours.in.month, by="month") %>%
      dplyr::mutate(emission.wperm2 = value * 0.000277778 / hours / area.m2) %>%
      {.}
  }
  heat.by.grid.monthly.comp
}

get.df.to.plot <- function(heat.by.grid.annual.comp, grid.geo=NULL, res="annual") {
  if (res == "annual") {
    heat.by.grid.annual = heat.by.grid.annual.comp %>%
      dplyr::group_by(id) %>%
      dplyr::summarise_if(is.numeric, sum) %>%
      dplyr::ungroup()
  } else if (res == "monthly") {
    heat.by.grid.annual = heat.by.grid.annual.comp %>%
      dplyr::group_by(id, month) %>%
      dplyr::summarise_if(is.numeric, sum) %>%
      dplyr::ungroup()
  }
  if (is.null(grid.geo)) {
    to.plot.ann.total <- heat.by.grid.annual
    to.plot.ann.component <- heat.by.grid.annual.comp
  } else {
    to.plot.ann.total <- heat.by.grid.annual %>%
      dplyr::left_join(grid.geo, by="id") %>%
      sf::st_as_sf() %>%
      {.}
    to.plot.ann.component <- heat.by.grid.annual.comp %>%
      dplyr::left_join(grid.geo, by="id") %>%
      sf::st_as_sf() %>%
      {.}
  }
  list(to.plot.ann.total, to.plot.ann.component)
}

get.grid.size.m2 <- function(spatial.level) {
  if (spatial.level == "finer") {
    return(500^2)
  } else {
    return(12000^2)
  }
}

get.grid.size.from.geometry <- function(grid.geo) {
  grid.geo$area.m2 <- sf::st_area(grid.geo)
  grid.no.geo <- grid.geo
  sf::st_geometry(grid.no.geo) <- NULL
  grid.no.geo <- grid.no.geo %>%
    tibble::as_tibble() %>%
    dplyr::mutate(area.m2 = as.numeric(area.m2)) %>%
    dplyr::select(id, area.m2)
  grid.no.geo
}

get.top.k.percent.emission <- function(df, k) {
  df.high.emit <- df %>%
    dplyr::filter(emission.wperm2 > quantile(df$emission.wperm2, probs = 1 - k / 100.0)) %>%
    {.}
  id.high.emit <- df.high.emit %>%
    tibble::as_tibble() %>%
    dplyr::distinct(id) %>%
    {.}
  list(df.high.emit, id.high.emit)
}

la.boundary = sf::st_read("domain/la-county-boundary.geojson", quiet=TRUE)
la.boundary.valid = sf::st_make_valid(la.boundary)
```

# Annual Total Heat Emission
## Summary Stats

```{r finerGridLevel, message=FALSE}
result = get.spatial.path.suf("finer")
spatial.path = result[[1]]
spatial.suf = result[[2]]
spatial.label = result[[3]]
grid.geo <- sf::st_read(sprintf("%s/wrf-grids-origin.geojson", spatial.path), quiet=TRUE)

df.area <- get.grid.size.from.geometry(grid.geo)

heat.by.grid.annual.comp = get.annual.data(time.pref="annual_2018", spatial.suf=spatial.suf, df.area)

## check grid size
## points <- tibble::tibble(lat = c(33.097332, 33.101246), lon = c(-118.65224, -118.65334))
## points.geo <- sf::st_as_sf(points, coords=c("lon", "lat"))
## line = sf::st_sfc(sf::st_linestring(rbind(c(-118.65224, 33.097332), c(-118.65334, 33.101246))), crs=4326)
## sf::st_length(line)

result = get.df.to.plot(heat.by.grid.annual.comp, grid.geo)
to.plot.ann.total = result[[1]]
to.plot.ann.component = result[[2]]

heat.by.grid.annual.comp %>%
  dplyr::group_by(variable) %>%
  dplyr::summarise_at(vars(emission.wperm2),
                      tibble::lst(min, "Q1"=~quantile(., probs = 0.25), mean,
                                  median, "Q3"=~quantile(., probs = 0.75),
                                  max)) %>%
  dplyr::ungroup() %>%
  knitr::kable(caption = "Finer Grid Annual Heat Emission Summary Statistics (W/m2)", digits = 3)
```

## Spatial distribution

```{r getSolarRadData, message=FALSE}
climate.data.path = "annual_WRF/M02_EnergyPlus_Forcing_Historical_LowRes_ann_2018"
## all grids using the same solar radiation data
solar.rad.grid.65 <- readr::read_csv(sprintf("%s/grids_csv/65.csv", climate.data.path)) %>%
  {.}

solar.rad.avg <- solar.rad.grid.65 %>%
  dplyr::summarise(solar.rad = mean(solar.rad))
```

For reference, the annual average solar radiation is `r round(solar.rad.avg, 2)` W/m2.

The following figure plots the average heat emission in W/m2. It's computed by
summing the total heat emission in each grid then dividing by the number of
hours in a year and the grid size in m2. The legends reflects the 10th to 90th
percentile of the heat emission.

```{r annHeatTotal, message=FALSE, fig.width=15, fig.height=7}
tm_shape(to.plot.ann.total) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "2018 Annual Heat Emission (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

The following plots shows the top 10 percent of the grids. The legend shows the 91th to the 99th percentile.

```{r annHeatTotalLarge, message=FALSE, fig.width=15, fig.height=7}
top.k.percent <- get.top.k.percent.emission(to.plot.ann.total, k=10)
top.k.percent.df <- top.k.percent[[1]]
top.k.percent.id <- top.k.percent[[2]]

tm_shape(top.k.percent.df) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "2018 Annual Heat Emission (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

## Building type composition of grids with high (top 10%) heat emission

The following table shows the building type composition for grid cells within the top 10% annual heat emission.

```{r largeIDTypeComp, message=FALSE}
building.info <- readr::read_csv("building_info_finer.csv")

idf.kw.to.usetype <- readr::read_csv("idf_kw_to_EnergyAtlas_usetype.csv") %>%
  dplyr::mutate_at(vars(usetype), recode, "res_total"="residential") %>%
  {.}

building.info <- building.info %>%
  dplyr::mutate_at(vars(building.type), recode,
                   "small single-family"="single-family",
                   "large single-family"="single-family",
                   "small multi-family"="multi-family",
                   "large multi-family"="multi-family") %>%
  dplyr::left_join(idf.kw.to.usetype, by="idf.kw")

building.info %>%
  dplyr::inner_join(top.k.percent.id, by="id") %>%
  dplyr::group_by(usetype) %>%
  dplyr::summarise(building.area.m2 = sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(desc(building.area.m2)) %>%
  knitr::kable(format="html", caption = "Building high-level type composition") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

```{r detaileTypeComp}
building.info %>%
  dplyr::inner_join(top.k.percent.id, by="id") %>%
  dplyr::group_by(building.type) %>%
  dplyr::summarise(building.area.m2 = sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(desc(building.area.m2)) %>%
  knitr::kable(format="html", caption = "Building type composition") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## Spatial distribution of heat emissions from different components in buildings 

The following figure shows the spatial distribution of total heat emissions for the five components.

```{r annHeatByComponent, message=FALSE, fig.width=15, fig.height=10}
tm_shape(to.plot.ann.component) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_facets(by="variable", ncol=3) +
  tm_layout(main.title = "Annual Heat Emission of the Five Component (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

## Spatial distribution of building surface heat emissions

The following plots the heat emission from building surface. The legends reflects the 10th to 90th percentile.

```{r annSurfHeat, message=FALSE, fig.width=15, fig.height=10}
tm_shape(to.plot.ann.component %>% filter(variable == "emission.surf")) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "Annual Building Surface Heat Emission (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

The following zooms in to the high-emission grids with surface heat emission above the 90th percentile. The legends reflects the 91th to 99th percentile.

```{r annSurfHeatHigh, message=FALSE, fig.width=15, fig.height=10}
top.k.percent.surf <- get.top.k.percent.emission(to.plot.ann.component %>% dplyr::filter(variable == "emission.surf"), k=10)
top.k.percent.surf.df <- top.k.percent.surf[[1]]
top.k.percent.surf.id <- top.k.percent.surf[[1]]

tm_shape(top.k.percent.surf.df) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "Annual Building Surface Heat Emission (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

## Building type composition of grids with high (top 10%) building surface heat emission

The following table shows the building type composition of grid cells with the top 10% building surface heat emission.

```{r largeSurfIDUseTypeComp, message=FALSE}
building.info %>%
  dplyr::inner_join(top.k.percent.surf.id, by="id") %>%
  dplyr::group_by(usetype) %>%
  dplyr::summarise(building.area.m2 = sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(desc(building.area.m2)) %>%
  knitr::kable(format="html", caption = "Building high-level type composition for grids with high surface heat emission") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

```{r largeSurfIDTypeComp, message=FALSE}
building.info %>%
  dplyr::inner_join(top.k.percent.surf.id, by="id") %>%
  dplyr::group_by(building.type) %>%
  dplyr::summarise(building.area.m2 = sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(desc(building.area.m2)) %>%
  knitr::kable(format="html", caption = "Building type composition for grids with high surface heat emission") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## Spatial distribution of building HVAC rejection heat emissions

The following plots the heat emission from building HVAC rejection. The legends reflects the 10th to 90th percentile.

```{r annRejHeat, message=FALSE, fig.width=15, fig.height=10}
tm_shape(to.plot.ann.component %>% filter(variable == "emission.rej")) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "Annual Building HVAC Rejection Heat Emission (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

The following zooms in to the high-emission group with HVAC rejection heat emission above the 90th percentile. The legends reflects the 91th to 99th percentile.

```{r annRejHeatHigh, message=FALSE, fig.width=15, fig.height=10}
top.k.percent.rej <- get.top.k.percent.emission(to.plot.ann.component %>% dplyr::filter(variable == "emission.rej"), k=10)
top.k.percent.rej.df <- top.k.percent.rej[[1]]
top.k.percent.rej.id <- top.k.percent.rej[[2]]

tm_shape(top.k.percent.rej.df) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "Annual Building HVAC Rejection Heat Emission (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)

if (!file.exists("high_annual_HVAC_rejection_grids.geojson")) {
  top.k.percent.rej.df %>%
    sf::st_write("high_annual_HVAC_rejection_grids.geojson")
  top.k.percent.surf.df %>%
    sf::st_write("high_annual_surface_heat_grids.geojson")
  top.k.percent.df %>%
    sf::st_write("high_annual_total_heat_grids.geojson")
}
```

## Building type composition of grids with high (top 10%) HVAC rejection heat emission

The following table shows the building type composition of grid cells with the top 10% building surface heat emission.

```{r largeRejIDUseTypeComp, message=FALSE}
building.info %>%
  dplyr::inner_join(top.k.percent.rej.id, by="id") %>%
  dplyr::group_by(usetype) %>%
  dplyr::summarise(building.area.m2 = sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(desc(building.area.m2)) %>%
  knitr::kable(format="html", caption = "Building high-level type composition for grids with high HVAC rejection heat emission") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

```{r largeRejIDTypeComp, message=FALSE}
building.info %>%
  dplyr::inner_join(top.k.percent.rej.id, by="id") %>%
  dplyr::group_by(building.type) %>%
  dplyr::summarise(building.area.m2 = sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(desc(building.area.m2)) %>%
  knitr::kable(format="html", caption = "Building type composition for grids with high HVAC rejection heat emission") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

# Monthly Profile

## Monthly heat emission averaged across grid cells

```{r monthly, message=FALSE, fig.width=15, fig.height=7}

heat.by.grid.monthly.comp = get.monthly.data(time.pref="annual_2018", spatial.suf=spatial.suf, df.area)

result = get.df.to.plot(heat.by.grid.monthly.comp, grid.geo=NULL, res = "monthly")
to.plot.monthly.total = result[[1]]
to.plot.monthly.component = result[[2]]

monthly.avg.emission <- to.plot.monthly.total %>%
  dplyr::mutate(month = as.numeric(month)) %>%
  dplyr::group_by(month) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  {.}

monthly.avg.emission %>%
  ggplot2::ggplot(ggplot2::aes(x = month, y = emission.wperm2)) +
  ggplot2::geom_point() +
  ggplot2::geom_line() +
  ggplot2::scale_x_continuous(breaks=1:12) +
  ggplot2::ggtitle(sprintf("Monthly Total Heat Emission Averaged Across %s", spatial.label)) +
  ggplot2::theme()
```

## Monthly heat emission by different components averaged across grid cells

The average heat emission from building surfaces remain the largest across most months of the year except for January and December. Surface heat emission peaks in May, while HVAC rejection heat emission peaks in July. Heat emission from exfiltration do not exhibit much seasonality and remain pretty steady across all months while there are some dips in the summer months for the average zong exhaust air heat loss and the HVAC relief air heat loss.

```{r monthlyAvg, message=FALSE, fig.width=15, fig.height=7}
monthly.avg.emission.component <- to.plot.monthly.component %>%
  dplyr::mutate(month = as.numeric(month)) %>%
  dplyr::group_by(month, variable) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  {.}

monthly.avg.emission.component %>%
  ggplot2::ggplot(ggplot2::aes(x = month, y = emission.wperm2, color=variable)) +
  ggplot2::geom_point() +
  ggplot2::geom_line() +
  ggplot2::scale_x_continuous(breaks=1:12) +
  ggplot2::ggtitle(sprintf("Monthly Heat Emission Component Averaged Across %s", spatial.label)) +
  ggplot2::theme()
```

## Spatial distribution of heat emissions in a winter month and a summer month

The following plot shows the January and July total heat emission
```{r monthlyTotal, message=FALSE, fig.width=15, fig.height=12}
jan.jul.monthly.avg.emission.component <- heat.by.grid.monthly.comp %>%
  dplyr::filter(month %in% c("01", "07")) %>%
  {.}

result = get.df.to.plot(jan.jul.monthly.avg.emission.component, grid.geo=grid.geo, res="monthly")
to.plot.jan.jul.total = result[[1]]
to.plot.jan.jul.component = result[[2]]

tm_shape(to.plot.jan.jul.total) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_facets(by="month") +
  tm_layout(main.title = "Jan and July Heat Emission (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

The following plot shows the January and July total heat emission for different components

```{r monthlyComp, message=FALSE, fig.width=15, fig.height=25}
tm_shape(to.plot.jan.jul.component) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_facets(by=c("variable", "month")) +
  tm_layout(main.title = "Jan and July Heat Emission",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

## July heat emission

### Total

The following figure shows the building heat emission in July. The legends reflects the 10th to the 90th percentile.

```{r july, message=FALSE, fig.width=15, fig.height=8}
to.plot.jul.total <- to.plot.jan.jul.total %>%
  dplyr::filter(month == "07")

tm_shape(to.plot.jul.total) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_facets(by="month") +
  tm_layout(main.title = "July Heat Emission (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

The following figure zooms to the grid cells with the top 10% building heat emission in July. The legends shows the 91th to the 99th percentile.

```{r julyTop, message=FALSE, fig.width=15, fig.height=8}
top.k.percent.july <- get.top.k.percent.emission(to.plot.jul.total, k=10)
top.k.percent.july.df <- top.k.percent.july[[1]]
top.k.percent.july.id <- top.k.percent.july[[2]]

tm_shape(top.k.percent.july.df) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_facets(by="month") +
  tm_layout(main.title = "July Heat Emission (W/m2)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

Building type composition for grids with high heat emission in July.

```{r julyType}
building.info %>%
  dplyr::inner_join(top.k.percent.july.id, by="id") %>%
  dplyr::group_by(usetype) %>%
  dplyr::summarise(building.area.m2 = sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(desc(building.area.m2)) %>%
  knitr::kable(format="html", caption = "Building high-level type composition of top heat emission grids in July") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

### Building surface heat emission 

This following figure shows the July building surface heat emission. The legends reflects the 10th to 90th percentile.

```{r julySurf, message=FALSE, fig.width=15, fig.height=8}
to.plot.jul.component <- to.plot.jan.jul.component %>%
  dplyr::filter(month == "07")

to.plot.jul.surf <- to.plot.jul.component %>%
  dplyr::filter(variable == "emission.surf")

tm_shape(to.plot.jul.surf) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "July Building Surface Heat Emission",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

The following figure shows the July surface heat emission top 91th to the 99th percentile.

```{r julySurfTop, message=FALSE, fig.width=15, fig.height=8}
top.k.percent.july.surf <- get.top.k.percent.emission(to.plot.jul.surf, k=10)
top.k.percent.july.surf.df <- top.k.percent.july[[1]]
top.k.percent.july.surf.id <- top.k.percent.july[[2]]

tm_shape(top.k.percent.july.surf.df) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "July Building Surface Heat Emission Top 10%",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

Building type composition for grids with high surface heat emission in July.

```{r julyTypeSurf}
building.info %>%
  dplyr::inner_join(top.k.percent.july.surf.id, by="id") %>%
  dplyr::group_by(usetype) %>%
  dplyr::summarise(building.area.m2 = sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(desc(building.area.m2)) %>%
  knitr::kable(format="html", caption = "Building high-level type composition of top surface heat emission grids in July") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

### HVAC rejection heat emission 

The figure visualizes the July HVAC rejection heat emission. The legends reflects the 10th to 90th percentile.

```{r julyRej, fig.width = 15, fig.height=8}
to.plot.jul.rej <- to.plot.jul.component %>%
  dplyr::filter(variable == "emission.rej")

tm_shape(to.plot.jul.rej) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "July Building HVAC Rejection Heat Emission",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

The figure shows the July HVAC rejection heat emission top 91th to the 99th percentile.

```{r julyRejTop, message=FALSE, fig.width=15, fig.height=8}
top.k.percent.july.rej <- get.top.k.percent.emission(to.plot.jul.rej, k=10)
top.k.percent.july.rej.df <- top.k.percent.july[[1]]
top.k.percent.july.rej.id <- top.k.percent.july[[2]]

tm_shape(top.k.percent.july.rej.df) +
  tm_polygons(col="emission.wperm2", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "July Building HVAC Rejction Heat Emission Top 10%",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

Building type composition for grids with high HVAC rejection heat emission in July.

```{r julyTypeRej}
building.info %>%
  dplyr::inner_join(top.k.percent.july.rej.id, by="id") %>%
  dplyr::group_by(usetype) %>%
  dplyr::summarise(building.area.m2 = sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(desc(building.area.m2)) %>%
  knitr::kable(format="html", caption = "Building high-level type composition of top HVAC heat rejection heat emission grids in July") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
