---
title: "2018 heat emission from EnergyPlus simulation"
author: "Yujie Xu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "~/Dropbox/workLBNL/EESA/code/im3-wrf/")
```
```{r dygraph, message=FALSE}
library("dplyr")

if (!file.exists("intermediate_data/annual_agg_by_time_by_idf_epw_2018.csv")) {
  df.sim.result <- readr::read_csv("intermediate_data/annual_sim_result_by_idf_epw_2018.csv")
  annual.sim.result <- df.sim.result %>%
    dplyr::group_by(idf.kw, epw.id) %>%
    dplyr::summarise_if(is.numeric, sum) %>%
    dplyr::ungroup() %>%
    {.}
  annual.sim.result %>%
    readr::write_csv("intermediate_data/annual_agg_by_time_by_idf_epw_2018.csv")
} else {
  annual.sim.result <- readr::read_csv("intermediate_data/annual_agg_by_time_by_idf_epw_2018.csv")
}
```

```{r annualSim, message=FALSE}
df.area.prototype = readr::read_csv("input_data/prototype_bldg_area.csv") %>%
  dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
  dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
  dplyr::select(-idf.name) %>%
  {.}

annual.sim.energy <- annual.sim.result %>%
  dplyr::select(idf.kw, epw.id, energy.overall)

annual.sim.EUI <- annual.sim.result %>%
  dplyr::left_join(df.area.prototype, by="idf.kw") %>%
  dplyr::mutate(EUI.kbtu.per.sqft = energy.overall * 1e-9 * 947.817 / (prototype.m2 * 10.7639)) %>%
  dplyr::mutate(EUI.GJ.per.m2 = energy.overall * 1e-9 / prototype.m2) %>%
  dplyr::mutate(emission.GJ.per.m2 = emission.overall * 1e-9 / prototype.m2) %>%
  {.}
```

The building with highest annual heat emission per building area are heavy manufacturing and
full service restaurant. They also have high energy use intensity.

```{r meanEUI, message=FALSE, fig.width=9, fig.height=10}
idf.kw.to.usetype <- readr::read_csv("input_data/idf_kw_to_EnergyAtlas_usetype.csv") %>%
  dplyr::mutate_at(vars(usetype), recode, "res_total"="residential") %>%
  {.}

annual.sim.EUI.avg <- annual.sim.EUI %>%
  dplyr::select(-epw.id) %>%
  dplyr::group_by(idf.kw) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  dplyr::select(idf.kw, EUI.GJ.per.m2, emission.GJ.per.m2) %>%
  tidyr::gather(variable, value, ends_with("per.m2"))

annual.sim.EUI.avg %>%
  dplyr::left_join(idf.kw.to.usetype, by="idf.kw") %>%
  dplyr::mutate_at(vars(variable), recode, "EUI.GJ.per.m2"="Electricity + Gas GJ/m2",
                   "emission.GJ.per.m2"="Heat Emission GJ/m2") %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, value), y=value, fill=interaction(variable, usetype))) +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ## ggplot2::scale_fill_grey(start=0.8, end=0.2) +
  ggplot2::scale_fill_brewer(palette = "Paired", direction=-1, name = "") +
  ggplot2::guides(fill=ggplot2::guide_legend(nrow=4)) +
  ggplot2::xlab("EnergyPlus input file") +
  ggplot2::ylab("Annual heat emission or energy consumption (GJ/m2)") +
  ggplot2::ggtitle("Prototype building annual energy and heat emission") +
  ggplot2::coord_flip() +
  ggplot2::theme(legend.position = "bottom")
```

```{r distributionEUI, message=FALSE, fig.width=9, fig.height=10}
annual.sim.EUI %>%
  dplyr::select(idf.kw, epw.id, EUI.GJ.per.m2, emission.GJ.per.m2) %>%
  tidyr::gather(variable, value, ends_with("per.m2")) %>%
  dplyr::mutate_at(vars(variable), recode, "EUI.GJ.per.m2"="Annual Electricity + Gas GJ/m2",
                   "emission.GJ.per.m2"="Annual Heat Emission GJ/m2") %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, value), y = value)) +
  ggplot2::geom_boxplot(outlier.size=0.5) +
  ggplot2::coord_flip() +
  ggplot2::ggtitle("Distribution of EnergyPlus total energy and total heat emission across different weather inputs") +
  ggplot2::ylab("EnergyPlus input file") +
  ggplot2::xlab("Annual heat emission or energy consumption (GJ/m2)") +
  ggplot2::facet_wrap(.~variable) +
  ggplot2::theme()
```

The ratio is computed for each idf-epw combination. The plot shows the average
across all different weather inputs. Single-family, multi-family, warehouse, and
small office have the largest heat-to-energy ratio. Even if the manufacturing
facility is adapted from warehouse model, they don't have the same high
heat-to-energy ratio as warehouse.

```{r euiHeatRatio, message=FALSE, fig.width=9, fig.height=10}
heat.eui.ratio <- annual.sim.EUI %>%
  dplyr::select(idf.kw, epw.id, ends_with("per.m2")) %>%
  dplyr::mutate(heat.over.energy = emission.GJ.per.m2 / EUI.GJ.per.m2) %>%
  {.}
heat.eui.ratio.avg <- heat.eui.ratio %>%
  dplyr::group_by(idf.kw) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  {.}

heat.eui.ratio.avg %>%
  dplyr::left_join(idf.kw.to.usetype, by="idf.kw") %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, heat.over.energy),
                               y = heat.over.energy,
                               label = sprintf("%0.1f", heat.over.energy), fill=usetype)) +
  ggplot2::geom_bar(stat="identity") +
  ggplot2::coord_flip() +
  ggplot2::geom_hline(yintercept = 1.0) +
  ggplot2::ggtitle("Ratio of heat emission over energy consumption") +
  ggplot2::xlab("EnergyPlus input file") +
  ggplot2::ylab("heat emission divided by energy consumption") +
  ggplot2::scale_fill_manual(values = rev(RColorBrewer::brewer.pal(name="Paired", n=8))[c(1, 3, 5, 7)]) +
  ggplot2::guides(fill=ggplot2::guide_legend(nrow=2)) +
  ggplot2::ylim(c(0, 16)) +
  ggplot2::geom_text(hjust=-0.1) +
  ggplot2::theme(legend.position = "bottom")
```

The ratio has pretty large variability for single family and warehouses.
Although some of the low variability might be hidden from the fact that some
building types don't exist in some grid cells.

```{r euiHeatRatioDistribution, message=FALSE, fig.width=9, fig.height=10}
heat.eui.ratio %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, heat.over.energy),
                               y = heat.over.energy)) +
  ggplot2::geom_boxplot(outlier.size = 0.5) +
  ggplot2::ggtitle("Distribution of ratio of heat emission over energy consumption") +
  ggplot2::xlab("EnergyPlus input file") +
  ggplot2::ylab("heat emission divided by energy consumption") +
  ggplot2::coord_flip() +
  ggplot2::theme()
```

