---
title: "2018 heat emission from EnergyPlus simulation"
author: "Yujie Xu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "~/Dropbox/workLBNL/EESA/code/im3-wrf/")
```
```{r dygraph, message=FALSE}
library("dplyr")

if (!file.exists("intermediate_data/annual_agg_by_time_by_idf_epw_2018.csv")) {
  df.sim.result <- readr::read_csv("intermediate_data/annual_sim_result_by_idf_epw_2018.csv")
  annual.sim.result <- df.sim.result %>%
    dplyr::group_by(idf.kw, epw.id) %>%
    dplyr::summarise_if(is.numeric, sum) %>%
    dplyr::ungroup() %>%
    {.}
  annual.sim.result %>%
    readr::write_csv("intermediate_data/annual_agg_by_time_by_idf_epw_2018.csv")
} else {
  annual.sim.result <- readr::read_csv("intermediate_data/annual_agg_by_time_by_idf_epw_2018.csv")
}
```

```{r annualSim, message=FALSE}
df.area.prototype = readr::read_csv("input_data/prototype_bldg_area.csv") %>%
  dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
  dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
  dplyr::select(-idf.name) %>%
  {.}

annual.sim.energy <- annual.sim.result %>%
  dplyr::select(idf.kw, epw.id, energy.overall)

annual.sim.EUI <- annual.sim.result %>%
  dplyr::left_join(df.area.prototype, by="idf.kw") %>%
  dplyr::mutate(EUI.kbtu.per.sqft = energy.overall * 1e-9 * 947.817 / (prototype.m2 * 10.7639)) %>%
  dplyr::mutate(EUI.GJ.per.m2 = energy.overall * 1e-9 / prototype.m2) %>%
  dplyr::mutate(emission.GJ.per.m2 = emission.overall * 1e-9 / prototype.m2) %>%
  {.}
```

The building with highest annual heat emission per building area are heavy manufacturing and
full service restaurant. They also have high energy use intensity.

```{r meanEUI, message=FALSE, fig.width=9, fig.height=10}
idf.kw.to.usetype <- readr::read_csv("input_data/idf_kw_to_EnergyAtlas_usetype.csv") %>%
  dplyr::mutate_at(vars(usetype), recode, "res_total"="residential") %>%
  {.}

annual.sim.EUI.avg <- annual.sim.EUI %>%
  dplyr::select(-epw.id) %>%
  dplyr::group_by(idf.kw) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  dplyr::select(idf.kw, EUI.GJ.per.m2, emission.GJ.per.m2) %>%
  tidyr::gather(variable, value, ends_with("per.m2"))

annual.sim.EUI.avg %>%
  dplyr::left_join(idf.kw.to.usetype, by="idf.kw") %>%
  dplyr::mutate_at(vars(variable), recode, "EUI.GJ.per.m2"="Electricity + Gas GJ/m2",
                   "emission.GJ.per.m2"="Heat Emission GJ/m2") %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, value), y=value, fill=interaction(variable, usetype))) +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ## ggplot2::scale_fill_grey(start=0.8, end=0.2) +
  ggplot2::scale_fill_brewer(palette = "Paired", direction=-1, name = "") +
  ggplot2::guides(fill=ggplot2::guide_legend(nrow=4)) +
  ggplot2::xlab("EnergyPlus input file") +
  ggplot2::ylab("Annual heat emission or energy consumption (GJ/m2)") +
  ggplot2::ggtitle("Prototype building annual energy and heat emission") +
  ggplot2::coord_flip() +
  ggplot2::theme(legend.position = "bottom")
```

```{r distributionEUI, message=FALSE, fig.width=9, fig.height=10}
annual.sim.EUI %>%
  dplyr::select(idf.kw, epw.id, EUI.GJ.per.m2, emission.GJ.per.m2) %>%
  tidyr::gather(variable, value, ends_with("per.m2")) %>%
  dplyr::mutate_at(vars(variable), recode, "EUI.GJ.per.m2"="Annual Electricity + Gas GJ/m2",
                   "emission.GJ.per.m2"="Annual Heat Emission GJ/m2") %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, value), y = value)) +
  ggplot2::geom_boxplot(outlier.size=0.5) +
  ggplot2::coord_flip() +
  ggplot2::ggtitle("Distribution of EnergyPlus total energy and total heat emission across different weather inputs") +
  ggplot2::ylab("EnergyPlus input file") +
  ggplot2::xlab("Annual heat emission or energy consumption (GJ/m2)") +
  ggplot2::facet_wrap(.~variable) +
  ggplot2::theme()
```

The ratio is computed for each idf-epw combination. The plot shows the average
across all different weather inputs. Single-family, multi-family, warehouse, and
small office have the largest heat-to-energy ratio. Even if the manufacturing
facility is adapted from warehouse model, they don't have the same high
heat-to-energy ratio as warehouse.

```{r euiHeatRatio, message=FALSE, fig.width=9, fig.height=10}
heat.eui.ratio <- annual.sim.EUI %>%
  dplyr::select(idf.kw, epw.id, ends_with("per.m2")) %>%
  dplyr::mutate(heat.over.energy = emission.GJ.per.m2 / EUI.GJ.per.m2) %>%
  {.}
heat.eui.ratio.avg <- heat.eui.ratio %>%
  dplyr::group_by(idf.kw) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  {.}

heat.eui.ratio.avg %>%
  dplyr::left_join(idf.kw.to.usetype, by="idf.kw") %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, heat.over.energy),
                               y = heat.over.energy,
                               label = sprintf("%0.1f", heat.over.energy), fill=usetype)) +
  ggplot2::geom_bar(stat="identity") +
  ggplot2::coord_flip() +
  ggplot2::geom_hline(yintercept = 1.0) +
  ggplot2::ggtitle("Ratio of heat emission over energy consumption") +
  ggplot2::xlab("EnergyPlus input file") +
  ggplot2::ylab("heat emission divided by energy consumption") +
  ggplot2::scale_fill_manual(values = rev(RColorBrewer::brewer.pal(name="Paired", n=8))[c(1, 3, 5, 7)]) +
  ggplot2::guides(fill=ggplot2::guide_legend(nrow=2)) +
  ggplot2::ylim(c(0, 16)) +
  ggplot2::geom_text(hjust=-0.1) +
  ggplot2::theme(legend.position = "bottom")
```

The ratio has pretty large variability for single family and warehouses.
Although some of the low variability might be hidden from the fact that some
building types don't exist in some grid cells.

```{r euiHeatRatioDistribution, message=FALSE, fig.width=9, fig.height=10}
heat.eui.ratio %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, heat.over.energy),
                               y = heat.over.energy)) +
  ggplot2::geom_boxplot(outlier.size = 0.5) +
  ggplot2::ggtitle("Distribution of ratio of heat emission over energy consumption") +
  ggplot2::xlab("EnergyPlus input file") +
  ggplot2::ylab("heat emission divided by energy consumption") +
  ggplot2::coord_flip() +
  ggplot2::theme()
```

Comparing with scorecards, using 3B weather file simulated on each building idf model

```{r cmpScorecards}
extract.float <- function(str) {
  stringr::str_extract(str, "([0-9]*[.])?[0-9]+")
}
extract.unit <- function(str) {
  stringr::str_extract(str, "\\[.*\\]")
}

read.area.energy.in.path <- function(filepath, suf, testing=FALSE) {
  files = list.files(filepath, pattern=suf)
  if (testing) {
    files = files[[1]]
  }
  results <- lapply(files, function(f) {
    lines = readLines(sprintf("%s/%s", filepath, f))
    area.line = which(stringr::str_detect(lines, "\\>Total Building Area\\<"))[[1]]
    area = as.numeric(extract.float(lines[[area.line + 1]]))
    energy.line = which(stringr::str_detect(lines, "\\>Total End Uses\\<"))[[1]]
    elec = as.numeric(extract.float(lines[[energy.line + 1]]))
    gas = as.numeric(extract.float(lines[[energy.line + 2]]))
    energy.unit = extract.unit(lines[(which(stringr::str_detect(lines, "End Uses"))[[1]] + 4)])
    area.unit = extract.unit(lines[(which(stringr::str_detect(lines, "\\>Total Building Area\\<"))[[1]] - 3)])
    tibble::tibble(area = area, area.unit = area.unit, elec = elec, gas = gas, energy.unit = energy.unit, filename = f)
  }) %>%
    dplyr::bind_rows() %>%
    {.}
  results
}

read.area.energy.commercial <- function(filepath, suf) {
  read.area.energy.in.path(filepath, suf) %>%
    tidyr::separate(filename, into=c("standard", "type", "version", "suf"), sep="_") %>%
    dplyr::select(-suf)
}

read.area.energy.residential <- function(filepath, suf) {
  read.area.energy.in.path(filepath, suf) %>%
    tidyr::separate(filename, into=c("country", "type", "climate", "system", "space", "suf"), sep="\\+") %>%
    dplyr::select(-country, -suf) %>%
    {.}
}

read.area.energy.ref.bld <- function(filepath, suf) {
  read.area.energy.in.path(filepath, suf) %>%
    tidyr::separate(filename, into=letters[1:8], sep="_") %>%
    dplyr::select(-(b:h)) %>%
    dplyr::rename(type = a) %>%
    dplyr::mutate(type = gsub("Pre1980", "", type)) %>%
    dplyr::mutate(type = gsub("RefBldg", "", type)) %>%
    {.}
}

results.ashrae.2013 = read.area.energy.commercial("input_data/scorecards/ASHRAE901_STD2013",
                                                  suf="*_ElPaso.table.htm")
results.iecc.2012 = read.area.energy.commercial("input_data/scorecards/IECC_STD2012",
                                                 suf="*_ElPaso.table.htm")

results.res = read.area.energy.residential("input_data/scorecards/resstd_CZ3B_IECC_2015", suf="2015.table.htm")

results.com.compile.2013 <- results.ashrae.2013 %>%
  dplyr::bind_rows(results.iecc.2012) %>%
  dplyr::mutate(elec.GJ.per.m2 = elec / area,
                gas.GJ.per.m2 = gas / area) %>%
  dplyr::select(type, elec.GJ.per.m2, gas.GJ.per.m2, standard, version) %>%
  dplyr::mutate(EUI.GJ.per.m2 = elec.GJ.per.m2 + gas.GJ.per.m2) %>%
  dplyr::mutate(source = "PNNL") %>%
  {.}

results.com.compile.2013 %>%
  readr::write_csv("intermediate_data/scorecards_GJ_m2_commercial_PNNL_2013.csv")

results.res.compile <- results.res %>%
  dplyr::mutate(elec.GJ.per.m2 = elec * 0.00105485 / (area * 0.092903),
                gas.GJ.per.m2 = gas  * 0.00105485 / (area * 0.092903)) %>%
  dplyr::mutate(standard = "IECC2015", version = sprintf("%s+%s", system, space)) %>%
  dplyr::select(type, elec.GJ.per.m2, gas.GJ.per.m2, standard, version) %>%
  dplyr::mutate_at(vars(type), recode, "SF"="SingleFamily", "MF"="MultiFamily") %>%
  dplyr::mutate(EUI.GJ.per.m2 = elec.GJ.per.m2 + gas.GJ.per.m2) %>%
  dplyr::mutate(source = "PNNL") %>%
  {.}

results.res.compile %>%
  dplyr::group_by(type) %>%
  dplyr::summarise_at(vars(EUI.GJ.per.m2),
                      tibble::lst(min, Q1=~quantile(., probs=0.25), mean, median, Q3=~quantile(., probs=0.75), max)) %>%
  dplyr::ungroup()

results.res.compile %>%
  readr::write_csv("intermediate_data/scorecards_GJ_m2_residential_PNNL_2015.csv")

annual.sim.EUI.avg %>%
  distinct(idf.kw) %>%
  print(n=Inf)

scorecards.compile <- results.res.compile %>%
  dplyr::filter(version == "gasfurnace+slab") %>%
  dplyr::bind_rows(results.com.compile) %>%
  ## tidyr::unite(source, standard:version) %>%
  dplyr::select(type, source, EUI.GJ.per.m2) %>%
  dplyr::mutate_at(vars(type), recode,
                   "RestaurantSitDown"="FullServiceRestaurant",
                   "HotelSmall"="SmallHotel",
                   "HotelLarge"="LargeHotel",
                   "OfficeSmall"="SmallOffice",
                   "OfficeMedium"="MediumOffice",
                   "OfficeLarge"="LargeOffice",
                   "ApartmentMidRise"="MidriseApartment",
                   "SchoolPrimary"="PrimarySchool",
                   "SchoolSecondary"="SecondarySchool") %>%
  {.}

annual.sim.EUI.avg.compile.2013 <- annual.sim.EUI.avg %>%
  tidyr::spread(variable, value) %>%
  dplyr::select(-emission.GJ.per.m2) %>%
  tidyr::separate(idf.kw, into=letters[1:6], sep="\\-") %>%
  dplyr::filter((b == "2013") | (c == "2013")) %>%
  dplyr::select(a, EUI.GJ.per.m2) %>%
  dplyr::rename(type = a) %>%
  dplyr::mutate(source = "this study") %>%
  {.}


## fixme: make this to function
compile.sim.result <- function(result.path, df.prototype.area) {
  folders <- list.files(result.path)
  result <- lapply(folders, function(folder) {
    df <- readr::read_csv(sprintf("%s/%s/eplusout.csv", result.path, folder)) %>%
      dplyr::mutate(energy.elec = `Electricity:Facility [J](Hourly)`) %>%
      dplyr::mutate(energy.overall = energy.elec) %>%
      {.}
    if ("NaturalGas:Facility [J](Hourly)" %in% names(df)) {
      df <- df %>%
        dplyr::mutate(energy.gas = `NaturalGas:Facility [J](Hourly)`) %>%
        dplyr::mutate(energy.overall = energy.elec + energy.gas)
    }
    df %>%
      dplyr::select(starts_with("energy")) %>%
      dplyr::summarise_if(is.numeric, sum) %>%
      dplyr::mutate(idf.kw = folder) %>%
      {.}
  }) %>%
    dplyr::bind_rows() %>%
    dplyr::mutate(energy.GJ = energy.overall * 1e-9) %>%
    dplyr::select(idf.kw, energy.GJ) %>%
    dplyr::left_join(df.prototype.area, by="idf.kw") %>%
    dplyr::mutate(EUI.GJ.per.m2 = energy.GJ / prototype.m2) %>%
    tidyr::separate(idf.kw, into=letters[1:6], sep="\\-") %>%
    dplyr::rename(type = a) %>%
    {.}
  result
}

prototype.area <- readr::read_csv("input_data/prototype_bldg_area.csv") %>%
  dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
  dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
  {.}

result.el.paso <- compile.sim.result("intermediate_data/EP_output/using_el_paso", prototype.area)

annual.sim.EUI.avg.compile.el.paso.2013 <- result.el.paso %>%
  dplyr::filter((b == "2013") | (c == "2013")) %>%
  dplyr::select(type, EUI.GJ.per.m2) %>%
  dplyr::mutate(source = "this study el paso") %>%
  na.omit() %>%
  {.}

  scorecards.compile %>%
  dplyr::group_by(type) %>%
  dplyr::summarise(EUI.GJ.per.m2 = mean(EUI.GJ.per.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(source = "scorecards") %>%
  dplyr::bind_rows(annual.sim.EUI.avg.compile.2013) %>%
  dplyr::bind_rows(annual.sim.EUI.avg.compile.el.paso.2013) %>%
  tidyr::spread(source, EUI.GJ.per.m2) %>%
  readr::write_csv("intermediate_data/cmp_sim_avg_scorecard_avg_2013.csv")

## single and multifamily has really large results

results.ref.pre1980 = read.area.energy.ref.bld("input_data/scorecards/refbldg_3b_usa_ca_los_angeles_pre1980_v1.3_5.0", suf=".htm")

results.com.compile.pre1980 <- results.ref.pre1980 %>%
  dplyr::mutate(elec.GJ.per.m2 = elec / area,
                gas.GJ.per.m2 = gas / area) %>%
  dplyr::select(type, elec.GJ.per.m2, gas.GJ.per.m2) %>%
  dplyr::mutate(EUI.GJ.per.m2 = elec.GJ.per.m2 + gas.GJ.per.m2) %>%
  dplyr::mutate(source = "NREL") %>%
  {.}

annual.sim.EUI.avg.compile.pre1980 <- annual.sim.EUI.avg %>%
  tidyr::spread(variable, value) %>%
  dplyr::select(-emission.GJ.per.m2) %>%
  tidyr::separate(idf.kw, into=letters[1:6], sep="\\-") %>%
  dplyr::filter(c == "1980") %>%
  dplyr::select(a, EUI.GJ.per.m2) %>%
  dplyr::rename(type = a) %>%
  dplyr::filter(type != "Religious") %>%
  dplyr::mutate(source = "this study") %>%
  {.}

result.la <- compile.sim.result("intermediate_data/EP_output/using_LA_tmy2", prototype.area)

annual.sim.EUI.avg.compile.la.pre1980 <- result.la %>%
  dplyr::filter(c == "1980") %>%
  dplyr::select(type, EUI.GJ.per.m2) %>%
  dplyr::mutate(source = "this study LA tmy2") %>%
  na.omit() %>%
  {.}

results.com.compile.pre1980 %>%
  dplyr::mutate_at(vars(type), recode,
                   "Stand-aloneRetail"="RetailStandalone") %>%
  dplyr::select(type, EUI.GJ.per.m2, source) %>%
  dplyr::bind_rows(annual.sim.EUI.avg.compile.pre1980) %>%
  dplyr::bind_rows(annual.sim.EUI.avg.compile.la.pre1980) %>%
  tidyr::spread(source, EUI.GJ.per.m2) %>%
  dplyr::filter(!is.na(`this study`)) %>%
  readr::write_csv("intermediate_data/cmp_sim_avg_scorecard_com_pre1980.csv")

```

```{r resstock}
df.restock = readr::read_tsv("input_data/resstock/metadata.tsv")

df.restock.la <- df.restock %>%
  dplyr::filter(in.resstock_county_id == "CA, Los Angeles County") %>%
  dplyr::filter(stringr::str_detect(in.geometry_building_type_recs, "-Family")) %>%
  dplyr::select(bldg_id,
                in.county,
                out.electricity.total.energy_consumption_intensity,
                out.natural_gas.total.energy_consumption_intensity,
                in.geometry_building_type_recs,
                in.vintage_acs,
                in.weather_file_TMY3) %>%
  dplyr::rename(elec = out.electricity.total.energy_consumption_intensity,
                gas = out.natural_gas.total.energy_consumption_intensity) %>%
  tidyr::separate(in.geometry_building_type_recs, into=c("type", "suf", "suf2"), sep="-") %>%
  dplyr::select(-suf, -suf2) %>%
  dplyr::mutate(type = sprintf("%sFamily", type)) %>%
  {.}

df.resstock.mod.vintage <- df.restock.la %>%
  dplyr::rename(vintage = in.vintage_acs) %>%
  {.}

get.resstock.summary <- function(df) {
  df %>%
    tidyr::gather(variable, kwh.per.sqft, elec:gas) %>%
    ## convert kwh/sqft to GJ/m2
    dplyr::mutate(EUI.GJ.per.m2 = kwh.per.sqft * 0.0036 / 0.092903) %>%
    dplyr::group_by(type, vintage) %>%
    dplyr::summarise_at(vars(EUI.GJ.per.m2),
                        tibble::lst(min, Q1=~quantile(., probs=0.25), mean, median, Q3=~quantile(., probs=0.75), `90th`=~quantile(., probs=0.90), max)) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(type, vintage) %>%
    {.}
}

get.resstock.summary.percentile <- function(df, prob) {
  df %>%
    tidyr::gather(variable, kwh.per.sqft, elec:gas) %>%
    ## convert kwh/sqft to GJ/m2
    dplyr::mutate(EUI.GJ.per.m2 = kwh.per.sqft * 0.0036 / 0.092903) %>%
    dplyr::group_by(type, vintage) %>%
    dplyr::summarise_at(vars(EUI.GJ.per.m2),
                        tibble::lst(percentile=~quantile(., probs=prob))) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(type, vintage) %>%
    {.}
}

resstock.summary <- get.resstock.summary(df.resstock.mod.vintage)

get.resstock.summary.percentile(df.resstock.mod.vintage, 0.85) %>%
  filter(type == "MultiFamily")

resstock.summary %>%
  readr::write_csv("intermediate_data/resstock_summary_stats.csv")

## get epw used in resstock for LA county

source("read_epw.R")

la.epw.base <- read.epw("input_data/M02_EnergyPlus_Forcing_Historical_LowRes/USA_CA_Los.Angeles.Intl.AP.722950_TMY3.epw")

## read resstock weather for LA county
la.weather.to.replace <- readr::read_csv("input_data/resstock/G0600370_tmy3.csv")

la.epw.base$DryBulb.C = la.weather.to.replace$`Dry Bulb Temperature [°C]`
la.epw.base$RelHum.percent = la.weather.to.replace$`Relative Humidity [%]`
la.epw.base$`WindSpd.m/s` = la.weather.to.replace$`Wind Speed [m/s]`
la.epw.base$WindDir.deg = la.weather.to.replace$`Wind Direction [Deg]`
la.epw.base$`GloHorzRad.Wh/m2` = la.weather.to.replace$`Global Horizontal Radiation [W/m2]`
la.epw.base$`DirNormRad.Wh/m2` = la.weather.to.replace$`Global Horizontal Radiation [W/m2]`
la.epw.base$`DifHorzRad.Wh/m2` = la.weather.to.replace$`Diffuse Horizontal Radiation [W/m2]`

la.epw.base %>%
  readr::write_csv("intermediate_data/resstock_weather_temp.csv")

lines = readLines("input_data/M02_EnergyPlus_Forcing_Historical_LowRes/USA_CA_Los.Angeles.Intl.AP.722950_TMY3.epw")
data.lines = readLines("intermediate_data/resstock_weather_temp.csv")

newlines = c(lines[1:8], data.lines[2:length( data.lines)])
writeLines(newlines, "intermediate_data/resstock/G0600370_tmy3.epw")

result.G0600370 <- compile.sim.result("intermediate_data/EP_output/using_G0600370", prototype.area)

result.G0600370.compile <- result.G0600370 %>%
  dplyr::mutate(vintage = ifelse(is.na(c), b, c)) %>%
  dplyr::mutate(vintage = ifelse(vintage == "LA", "-", vintage)) %>%
  dplyr::mutate(vintage = ifelse(vintage == "1980", "pre-1980", vintage)) %>%
  dplyr::select(vintage, type, EUI.GJ.per.m2) %>%
  na.omit() %>%
  {.}

result.G0600370.compile %>%
  readr::write_csv("intermediate_data/sim_EUI_with_resstock_comstock_weather.csv")

```

ComStock

```{r comstock}
df.comtock = readr::read_tsv("input_data/comstock/metadata.tsv")

df.comtock.la <- df.comtock %>%
  dplyr::filter(in.state_abbreviation == "CA") %>%
  dplyr::filter(in.resstock_county_id == "CA, Los Angeles County") %>%
  dplyr::select(bldg_id,
                in.county,
                out.electricity.total.energy_consumption_intensity,
                out.natural_gas.total.energy_consumption_intensity,
                in.building_type,
                in.energy_code_followed_during_original_building_construction,
                in.weather_file_TMY3) %>%
  dplyr::rename(elec = out.electricity.total.energy_consumption_intensity,
                gas = out.natural_gas.total.energy_consumption_intensity,
                type = in.building_type) %>%
  dplyr::mutate(vintage = gsub("ComStock DEER ", "", in.energy_code_followed_during_original_building_construction)) %>%
  {.}

comstock.summary <- get.resstock.summary(df.comtock.la)

comstock.summary %>%
  readr::write_csv("intermediate_data/comstock_summary_stats.csv")

comstock.summary %>%
  dplyr::rename(vintage.comstock = vintage) %>%
  dplyr::mutate(vintage = case_when(vintage.comstock %in% c("1985", "1996", "2003", "2007") ~ "2004",
                                    vintage.comstock %in% c("2011", "2014", "2015", "2017") ~ "2013",
                                    (vintage.comstock == "Pre-1975") ~ "pre-1980")) %>%
  dplyr::inner_join(result.G0600370.compile, by=c("type", "vintage")) %>%
  readr::write_csv("intermediate_data/cmp_comstock_this_study_EUI.csv")
```
