---
title: "Verify Residential"
author: "Yujie Xu"
date: "6/1/2022"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "~/Dropbox/workLBNL/EESA/code/im3-wrf/rmd")
```

## Residential building simulation results compared against scorecards

```{r cmpScorecard, message=FALSE, warning=FALSE}

library("dplyr")
library("tmap")
library("ggpmisc")
firstRun = FALSE
if (firstRun) {
  df.ann <- readr::read_csv("../annual_sim_result_by_idf_epw.csv")

  df.area.prototype = readr::read_csv("../prototype_bldg_area.csv") %>%
    dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
    dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
    dplyr::select(-idf.name) %>%
    {.}

  df.vin.type.idf <- readr::read_csv("../type_vintage_to_idf_mapping.csv") %>%
    dplyr::select(-building.count) %>%
    dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
    dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
    {.}

  df.sim.ann.eui <- df.ann %>%
    dplyr::mutate(energy.elec.GJ = energy.elec * 1e-9) %>%
    dplyr::mutate(energy.gas.GJ = energy.gas * 1e-9) %>%
    dplyr::group_by(idf.kw, epw.id) %>%
    dplyr::summarise_at(vars(energy.elec.GJ, energy.gas.GJ), sum) %>%
    dplyr::ungroup() %>%
    dplyr::left_join(df.area.prototype, by="idf.kw") %>%
    dplyr::mutate(elec.GJ.per.m2 = energy.elec.GJ / prototype.m2,
                  gas.GJ.per.m2 = energy.gas.GJ / prototype.m2) %>%
    dplyr::left_join(df.vin.type.idf, by="idf.kw") %>%
    {.}

  df.sim.ann.eui %>%
    readr::write_csv("sim_ann.csv")

} else {
  df.sim.ann.eui = readr::read_csv("sim_ann.csv")
}

df.sim.ann.eui.res.long <- df.sim.ann.eui %>%
  tidyr::separate(idf.kw, into=c("usetype", "suffix"), sep="-", remove=FALSE) %>%
  dplyr::filter(usetype %in% c("SingleFamily", "MultiFamily")) %>%
  dplyr::group_by(usetype, vintage) %>%
  dplyr::summarise_at(vars(elec.GJ.per.m2, gas.GJ.per.m2), mean) %>%
  dplyr::ungroup() %>%
  tidyr::gather(fuel, GJ.per.m2, ends_with("per.m2")) %>%
  dplyr::mutate_at(vars(fuel), recode, "elec.GJ.per.m2"="Electricity",
                   "gas.GJ.per.m2"="Gas") %>%
  dplyr::mutate(data.source = "simulation") %>%
  {.}

df.iecc.scorecard = readr::read_csv("../scorecard/IECC_res_9-5.csv")

df.iecc.scorecard.res.long <- df.iecc.scorecard %>%
  select(type, vintage, data.source, ends_with("kBtu"), ft2) %>%
  tidyr::gather(status, kBtu, ends_with("kBtu")) %>%
  tidyr::separate(status, into=c("fuel", "unit"), sep="\\.") %>%
  dplyr::select(-unit) %>%
  dplyr::mutate(GJ.per.m2 = kBtu * 0.0010551 / (ft2 * 0.092903)) %>%
  dplyr::select(type, vintage, fuel, GJ.per.m2, data.source) %>%
  dplyr::rename(usetype = type) %>%
  {.}

## unit is GJ per m2
df.sim.ann.eui.res.long %>%
  dplyr::bind_rows(df.iecc.scorecard.res.long) %>%
  dplyr::arrange(usetype, vintage, fuel, data.source) %>%
  dplyr::select(usetype, vintage, fuel, data.source, everything()) %>%
  tidyr::spread(data.source, GJ.per.m2) %>%
  dplyr::mutate(simulation.over.ref = ifelse(is.na(SangHoon), simulation / `IECC_res_9-5`, simulation / SangHoon)) %>%
  knitr::kable(digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

From the comparison above with PNNL reference models and SangHoon's model for the pre-1980 single-family homes, our simulation results are either equal or lower than the reference models.

According to this https://portfoliomanager.energystar.gov/pdf/reference/US%20National%20Median%20Table.pdf, Multifamily Housing has a site EUI of 59.6 kBtu/sqft, which is about 0.68 GJ/m2, about twice of the reference models and our simulation.

According to RECS West region energy usage in https://www.eia.gov/consumption/residential/data/2015/c&e/pdf/ce2.5.pdf table and building size in https://www.eia.gov/consumption/residential/data/2015/hc/php/hc10.5.php, 
the site electricity and gas consumption is as follows. The consumption are higher than the PNNL and our simulation results.

```{r recsTable, message=FALSE}
df.recs <- tibble::tibble(building.type = c("Single-family detached", "Single-family attached",
                                            "Apartments in buildings with 2–4 units", "Apartments in buildings with 5 or more units"),
                          Electricity.kBtu = c(35200, 23300, 17700, 15600),
                          Gas.kBtu = c(49900, 32200, 24400, 15400),
                          million.housing.units = c(16.2, 1.6, 1.9, 5.3),
                          billion.sqft = c(37.2, 2.4, 1.7, 4.4))

df.recs %>%
  dplyr::mutate(avg.building.sqft = billion.sqft * 1000 / million.housing.units) %>%
  dplyr::mutate(Electricity.GJ.per.m2 = Electricity.kBtu * 0.0010551 / (avg.building.sqft * 0.092903),
                Gas.GJ.per.m2 = Gas.kBtu * 0.0010551 / (avg.building.sqft * 0.092903)) %>%
  knitr::kable(digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

```{r readResSimData, message=FALSE, warning=FALSE}

la.energy <- readr::read_csv("../energyAtlas/usage_bld_kwh.csv")

la.energy.nb <- la.energy %>%
  tidyr::separate(geo_id, c("id.type", "id.num")) %>%
  dplyr::filter(id.type == "neighborhoods") %>%
  dplyr::mutate(id.num = as.numeric(id.num)) %>%
  {.}

nb.valid.data <- la.energy.nb %>%
  dplyr::filter(usetype %in% c("single_family", "multi_family")) %>%
  dplyr::filter(usage != "masked") %>%
  dplyr::mutate(usage = as.numeric(usage)) %>%
  distinct(id.num) %>%
  {.}

if (firstRun) {
  result.ann <- readr::read_csv("../annual_sim_result_by_idf_epw.csv")
  annual.total.result <- result.ann %>%
    dplyr::group_by(idf.kw, epw.id) %>%
    dplyr::summarise_if(is.numeric, sum) %>%
    dplyr::ungroup() %>%
    dplyr::select(idf.kw, epw.id, energy.overall, energy.elec, energy.gas) %>%
    dplyr::mutate(epw.id = as.numeric(epw.id)) %>%
    {.}
  annual.total.result %>%
    readr::write_csv("../annual_total_result.csv")
} else {
  annual.total.result <- readr::read_csv("../annual_total_result.csv")
}

building.info <- readr::read_csv("../building_info.csv")

building.nb.match = readr::read_csv("../building_id_to_neighborhood.csv")

sim.ann.nb.join <- building.nb.match %>%
  tibble::as_tibble() %>%
  dplyr::filter(!is.na(neighborho)) %>%
  dplyr::inner_join(building.info, by="OBJECTID") %>%
  dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
  dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
  dplyr::inner_join(annual.total.result, by=c("idf.kw", "epw.id")) %>%
  dplyr::mutate(energy.kwh = energy.overall * 1e-9 * 277.778) %>%
  dplyr::mutate(elec.kwh = energy.elec * 1e-9 * 277.778,
                gas.kwh = energy.gas * 1e-9 * 277.778) %>%
  {.}
```

From the CEC Electricity Consumption by County webpage, https://ecdms.energy.ca.gov/elecbycounty.aspx
the total electricity consumption of total, residential, and non-residential buildings are as follows.

```{r cmpCEC, message=FALSE, warning=FALSE}
df.cec = readr::read_csv("../CECdata/ElectricityByCounty_2018.csv")

df.cec %>%
  dplyr::select(-`2018`) %>%
  dplyr::rename(`Total Usage Gwh`=`Total Usage`) %>%
  knitr::kable(caption = "CEC total electricity usage in LA county (million kwh)") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

sim.ann.nb.join %>%
  dplyr::summarise_at(vars(ends_with("kwh")), sum) %>%
  dplyr::mutate_at(vars(ends_with("kwh")), function(x) {x/1e6}) %>%
  dplyr::rename_with(~gsub("kwh", "Gwh", .x), ends_with("kwh")) %>%
  knitr::kable(caption = "Total consumption of all building types, restricted to neighborhoods with valid data") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

sim.ann.nb.join %>%
  dplyr::filter(stringr::str_detect(idf.kw, "Family")) %>%
  dplyr::summarise_at(vars(ends_with("kwh")), sum) %>%
  dplyr::mutate_at(vars(ends_with("kwh")), function(x) {x/1e6}) %>%
  dplyr::rename_with(~gsub("kwh", "Gwh", .x), ends_with("kwh")) %>%
  knitr::kable(caption = "Total consumption of residential buildings") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## Compare with EnergyAtlas residential building stock, with masked data removed
Join neighborhood or census tract with building.

Restrict to single and multi-family

Remove neighborhood or census tract with masked data or zero sqft with single or multi family usetypes.

```{r compileNbTractData, message=FALSE, warning=FALSE}
sim.ann.nb.join.res <- sim.ann.nb.join %>%
  dplyr::filter(stringr::str_detect(idf.kw, "Family-")) %>%
  dplyr::filter(neighborho %in% nb.valid.data$id.num) %>%
  {.}

sim.ann.agg.to.nb.use.res <- sim.ann.nb.join.res %>%
  tidyr::separate(idf.kw, into=c("usetype", "suffix"), sep="-", remove=FALSE) %>%
  dplyr::select(-suffix) %>%
  dplyr::group_by(neighborho, usetype) %>%
  summarise_at(vars(energy.kwh, building.area.m2, FootprintArea.m2), sum) %>%
  dplyr::ungroup() %>%
  {.}

building.to.census.tract <- readr::read_csv("../building_id_to_census_tract.csv")

## no negative usage for single and multi family buildings in census tract data
sim.ann.tract.join <- building.to.census.tract %>%
  tibble::as_tibble() %>%
  dplyr::inner_join(building.info, by="OBJECTID") %>%
  dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
  dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
  dplyr::inner_join(annual.total.result, by=c("idf.kw", "epw.id")) %>%
  dplyr::mutate(energy.kwh = energy.overall * 1e-9 * 277.778) %>%
  {.}

sim.ann.tract.join.res <- sim.ann.tract.join %>%
  dplyr::filter(stringr::str_detect(idf.kw, "Family-")) %>%
  {.}

sim.ann.agg.to.tract.use.res <- sim.ann.tract.join.res %>%
  tidyr::separate(idf.kw, into=c("usetype", "suffix"), sep="-", remove=FALSE) %>%
  dplyr::select(-suffix) %>%
  dplyr::group_by(GEOID, usetype) %>%
  summarise_at(vars(energy.kwh, building.area.m2, FootprintArea.m2), sum) %>%
  dplyr::ungroup() %>%
  {.}

nb.with.bd <- building.nb.match %>%
  tibble::as_tibble() %>%
  dplyr::filter(!is.na(neighborho)) %>%
  dplyr::inner_join(building.info, by="OBJECTID") %>%
  dplyr::distinct(neighborho) %>%
  {.}

## restrict to grids with buildings
la.energy.nb.withinLA <- la.energy.nb %>%
  dplyr::inner_join(nb.with.bd, by=c("id.num"="neighborho")) %>%
  {.}
## remove masked
la.energy.nb.not.masked <- la.energy.nb.withinLA %>%
  dplyr::filter(usage != "masked") %>%
  dplyr::mutate(usage = as.numeric(usage)) %>%
  {.}
## sqft > 0
la.energy.nb.positive.size <- la.energy.nb.not.masked %>%
  dplyr::filter(sqft > 0) %>%
  {.}
## not in agriculture or other usetype
la.energy.nb.use.total.res <- la.energy.nb.positive.size %>%
  dplyr::filter(usetype %in% c("single_family", "multi_family")) %>%
  dplyr::select(id.num, usetype, sqft, usage) %>%
  dplyr::mutate(data.source = "Energy Atlas 2016",
                m2 = sqft * 0.092903) %>%
  dplyr::select(id.num, usetype, usage, m2, data.source) %>%
  dplyr::mutate_at(vars(usetype), recode, "single_family"="SingleFamily",
                   "multi_family"="MultiFamily") %>%
  {.}

df.tract.energy <- readr::read_csv("../energyAtlas/Census Tract/kwh_annual.csv") %>%
  dplyr::filter(usage > 0, sqft > 0) %>%
  {.}

df.tract.energy.agg.filter <- df.tract.energy %>%
  dplyr::filter(year == 2016) %>%
  dplyr::select(-year) %>%
  dplyr::group_by(geoid, usetype) %>%
  dplyr::summarise_at(vars(usage, sqft), sum) %>%
  dplyr::ungroup() %>%
  dplyr::mutate_at(vars(usetype), recode, "single_family"="SingleFamily",
                   "multi_family"="MultiFamily") %>%
  dplyr::mutate(data.source = "Energy Atlas 2016",
                m2 = sqft * 0.092903) %>%
  dplyr::select(geoid, usetype, usage, m2, data.source) %>%
  dplyr::rename(id.num=geoid) %>%
  {.}

df.tract.energy.agg.filter.res <- df.tract.energy.agg.filter %>%
  dplyr::filter(usetype %in% c("SingleFamily", "MultiFamily")) %>%
  {.}

total.ann.nb.use.cmp <- sim.ann.agg.to.nb.use.res %>%
  dplyr::select(neighborho, usetype, energy.kwh, building.area.m2) %>%
  dplyr::rename(id.num=neighborho, usage=energy.kwh, m2=building.area.m2) %>%
  dplyr::mutate(data.source = "Simulation 2018") %>%
  dplyr::bind_rows(la.energy.nb.use.total.res) %>%
  dplyr::group_by(id.num, usetype) %>%
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup() %>%
  {.}

to.plot.total.ann.use.cmp <- total.ann.nb.use.cmp %>%
  dplyr::mutate(kwh.per.m2 = usage / m2) %>%
  tidyr::gather(variable, value, c(usage, m2, kwh.per.m2)) %>%
  tidyr::spread(data.source, value) %>%
  {.}

```
We have slightly higher single-to-multi-family ratio

```{r vis, message=FALSE}
area.ratio.of.usetypes <- to.plot.total.ann.use.cmp %>%
  dplyr::filter(variable == "m2") %>%
  dplyr::select(-variable) %>%
  tidyr::gather(data.source, m2, `Energy Atlas 2016`:`Simulation 2018`) %>%
  dplyr::group_by(id.num, data.source) %>%
  dplyr::mutate(total.m2 = sum(m2)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(ratio = m2 / total.m2) %>%
  {.}

area.ratio.of.usetypes %>%
  dplyr::select(-m2, -total.m2) %>%
  tidyr::spread(data.source, ratio) %>%
  dplyr::mutate(ratio.diff = `Simulation 2018` - `Energy Atlas 2016`) %>%
  ggplot2::ggplot(ggplot2::aes(x = usetype, y=ratio.diff)) +
  ggplot2::geom_violin() +
  ggplot2::geom_boxplot(width = 0.1, outlier.shape = NA) +
  ggplot2::geom_jitter(size = 0.1) +
  ggplot2::coord_flip() +
  ggplot2::ggtitle("Compare (simulation usetype ratio - Energy Atlas usetype ratio) difference for Single-Family and Multi-Family") +
  ggplot2::theme()
```

## Compare Xuan's total building area in census tract with mine and EnergyAtlas

Xuan seems to produce grid-level normalized results by normalizing against total building footprint area (the 'floor_area' in https://github.com/LBNL-ETA/im3-wrf/blob/main/4_post_process.ipynb)

```{r XuanBuildingInfo, message=FALSE}
if (firstRun) {
  xuan.la.buildings <- sf::st_read("../bldg-wrf-mapping_old data wrong grid/la-all-bldgs-2229-wrf-area-filtered.geojson")
  xuan.la.buildings.centroid <- sf::st_centroid(xuan.la.buildings)
  xuan.building.tract <- sf::st_join(xuan.la.buildings.centroid, tract.ca.2229, join = sf::st_within) %>%
    {.}
  xuan.building.tract.nogeom <- xuan.building.tract %>%
    {.}
  sf::st_geometry(xuan.building.tract.nogeom) <- NULL
  usecode.to.usetype <- readr::read_csv("../bldg-wrf-mapping_old data wrong grid/use-code-map-simple.csv",
                                        col_names = c("UseCode14", "building.type"), skip=1) %>%
    {.}
  xuan.building.metadata <- xuan.building.tract.nogeom %>%
    tibble::as_tibble() %>%
    dplyr::filter(!is.na(GEOID)) %>%
    dplyr::select(`BLD_ID`, OBJECTID, GEOID, `UseCode14`, area_sqft, total_area_sqft, NoStorey) %>%
    dplyr::left_join(usecode.to.usetype, by="UseCode14") %>%
    dplyr::filter(building.type %in% c("SF", "MF")) %>%
    {.}
  xuan.building.metadata %>%
    readr::write_csv("xuan_building_metadata.csv")
} else {
  xuan.building.metadata <- readr::read_csv("xuan_building_metadata.csv", guess_max = 40000)
}

xuan.building.area <- xuan.building.metadata %>%
  dplyr::mutate(m2 = total_area_sqft * 0.092903) %>%
  dplyr::group_by(GEOID, building.type) %>%
  ## "area_sqft": building footprint area...
  ## "total_area_sqft": building total area
  dplyr::summarize_at(vars(m2), sum) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(usetype = case_when(building.type == "SF"~"SingleFamily",
                                    TRUE ~ "MultiFamily")) %>%
  dplyr::mutate(data.source = "Xuan building area") %>%
  dplyr::rename(id.num=GEOID) %>%
  dplyr::select(id.num, usetype, m2, data.source) %>%
  {.}

xuan.building.footprint <- xuan.building.metadata %>%
  dplyr::mutate(m2 = area_sqft * 0.092903) %>%
  dplyr::group_by(GEOID, building.type) %>%
  ## "area_sqft": building footprint area...
  ## "total_area_sqft": building total area
  dplyr::summarize_at(vars(m2), sum) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(usetype = case_when(building.type == "SF"~"SingleFamily",
                                    TRUE ~ "MultiFamily")) %>%
  dplyr::mutate(data.source = "Xuan building footprint") %>%
  dplyr::rename(id.num=GEOID) %>%
  dplyr::select(id.num, usetype, m2, data.source) %>%
  {.}

xuan.building.metadata %>%
  head() %>%
  knitr::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

We take both the "area_sqft" and "total_area_sqft" column and do the comparison. In Xuan's code "area_sqft" means building footprint size, "area_sqft_total" means building size

## Compare the census tract level total building size between EnergyAtlas and simulation for single and multi-family buildings, restricted to the census tracts with data in both data sources

```{r cmpAreaUsetypeTract, fig.show="hold", out.width="33%", message=FALSE, eval=TRUE}
total.ann.tract.use.cmp <- sim.ann.agg.to.tract.use.res %>%
  dplyr::select(GEOID, usetype, energy.kwh, building.area.m2) %>%
  dplyr::rename(id.num=GEOID, usage=energy.kwh, m2=building.area.m2) %>%
  dplyr::mutate(data.source = "Simulation 2018") %>%
  dplyr::bind_rows(df.tract.energy.agg.filter.res) %>%
  dplyr::bind_rows(xuan.building.area) %>%
  dplyr::bind_rows(xuan.building.footprint) %>%
  dplyr::group_by(id.num, usetype) %>%
  dplyr::filter(n() == 4) %>%
  dplyr::ungroup() %>%
  {.}

to.plot.total.ann.use.tract.cmp <- total.ann.tract.use.cmp %>%
  dplyr::mutate(kwh.per.m2 = usage / m2) %>%
  tidyr::gather(variable, value, c(usage, m2, kwh.per.m2)) %>%
  tidyr::spread(data.source, value) %>%
  {.}

tract.ca <- sf::st_read("../domain/tl_2019_06_tract/tl_2019_06_tract.shp") %>%
  dplyr::select(GEOID, NAME) %>%
  {.}

tract.ca.2229 <- sf::st_transform(tract.ca, crs=2229)

usetypes = c("SingleFamily", "MultiFamily")
labels = c("Single-Family", "Multi-Family")

## upper.lims = c(1.5e7, 8e6, 2.5e5, 5e6)
upper.lims = c(1e6, 5e5)

for (i in seq_along(usetypes)) {
  p1 <- to.plot.total.ann.use.tract.cmp %>%
    dplyr::filter(variable == "m2", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, y=`Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ## ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                            after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("Mine vs EnergyAtlas %s total building area (m2)", labels[[i]])) +
    ## ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::xlim(0, upper.lims[[i]]) +
    ggplot2::ylim(0, upper.lims[[i]]) +
    ggplot2::theme()
  print(p1)
  p2 <- to.plot.total.ann.use.tract.cmp %>%
    dplyr::filter(variable == "m2", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Xuan building area`, y=`Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ## ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                   after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("Xuan building area vs EnergyAtlas %s total building area (m2)", labels[[i]])) +
    ## ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::xlim(0, upper.lims[[i]]) +
    ggplot2::ylim(0, upper.lims[[i]]) +
    ggplot2::theme()
  print(p2)
  p3 <- to.plot.total.ann.use.tract.cmp %>%
    dplyr::filter(variable == "m2", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Xuan building footprint`, y=`Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ## ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                            after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("Xuan building footprint vs EnergyAtlas %s total building area (m2)", labels[[i]])) +
    ## ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::xlim(0, upper.lims[[i]]) +
    ggplot2::ylim(0, upper.lims[[i]]) +
    ggplot2::theme()
  print(p3)
}
```

```{r cmpAreaUsetypeTractMapLim, fig.show="hold", out.width="100%", message=FALSE, eval=TRUE}
upper.lims = c(1e6, 5e5)
for (i in seq_along(usetypes)) {
  p4 <- total.ann.tract.use.cmp %>%
    ## restrict the range to be same as the scatter plots
    dplyr::filter(m2 <= upper.lims[[i]]) %>%
    dplyr::filter(usetype == usetypes[[i]]) %>%
    dplyr::inner_join(tract.ca, by=c("id.num"="GEOID")) %>%
    tibble::as_tibble() %>%
    sf::st_as_sf() %>%
    ## ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
    tm_shape() +
    tm_polygons("m2", n=5, style="quantile", palette="Purples") +
    tm_facets(by="data.source") +
    tm_layout(main.title = sprintf("Building size for %s (m2)", labels[[i]]),
              main.title.size = 1.2,
              legend.position=c("left", "bottom"), legend.outside=FALSE)
  print(p4)
}
```

Following is the same set of plots but without removal of outliers

```{r cmpXuanMineEnergyAtlas, , fig.show="hold", out.width="33%", message=FALSE}
## upper.lims = c(1.5e7, 8e6, 2.5e5, 5e6)
upper.lims = c(NA, NA)

for (i in seq_along(usetypes)) {
  p1 <- to.plot.total.ann.use.tract.cmp %>%
    dplyr::filter(variable == "m2", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, y=`Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ## ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                            after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("Mine vs EnergyAtlas %s total building area (m2)", labels[[i]])) +
    ## ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::xlim(0, upper.lims[[i]]) +
    ggplot2::ylim(0, upper.lims[[i]]) +
    ggplot2::theme()
  print(p1)
  p2 <- to.plot.total.ann.use.tract.cmp %>%
    dplyr::filter(variable == "m2", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Xuan building area`, y=`Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ## ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                   after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("Xuan building area vs EnergyAtlas %s total building area (m2)", labels[[i]])) +
    ## ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::xlim(0, upper.lims[[i]]) +
    ggplot2::ylim(0, upper.lims[[i]]) +
    ggplot2::theme()
  print(p2)
  p3 <- to.plot.total.ann.use.tract.cmp %>%
    dplyr::filter(variable == "m2", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Xuan building footprint`, y=`Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ## ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                            after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("Xuan building footprint vs EnergyAtlas %s total building area (m2)", labels[[i]])) +
    ## ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::xlim(0, upper.lims[[i]]) +
    ggplot2::ylim(0, upper.lims[[i]]) +
    ggplot2::theme()
  print(p3)
}
```

Exploring the outliers

```{r outlierExamine, message=FALSE}
to.plot.total.ann.use.tract.cmp %>%
  dplyr::filter(variable == "m2", usetype == "SingleFamily") %>%
  dplyr::filter(`Xuan building area` > 2.7e8) %>%
  ggplot2::ggplot(ggplot2::aes(x = `Xuan building area`, y = `Energy Atlas 2016`)) +
  ggplot2::ggtitle("Visualize outliers above x > 2.7e8") +
  ggplot2::geom_point()

outlier.tracts <- to.plot.total.ann.use.tract.cmp %>%
  dplyr::filter(variable == "m2", usetype == "SingleFamily") %>%
  dplyr::filter(`Xuan building area` > 2.7e8) %>%
  distinct(id.num) %>%
  {.}

tracts.with.data <- tract.ca %>%
  dplyr::filter(GEOID %in% to.plot.total.ann.use.tract.cmp$id.num)

outlier.tracts %>%
  dplyr::left_join(tract.ca, by=c("id.num"="GEOID")) %>%
  sf::st_as_sf() %>%
  ggplot2::ggplot() +
  ggplot2::geom_sf(fill = "blue") +
  ggplot2::ggtitle("The census tracts with ouliers (blue ones)") +
  ggplot2::geom_sf(data = tracts.with.data, fill = NA)

print("single and multi-family homes")
xuan.building.metadata %>%
  dplyr::filter(GEOID %in% outlier.tracts$id.num) %>%
  dplyr::mutate_if(is.character, as.factor) %>%
  summary()

print("restricted to single family homes")
xuan.building.metadata %>%
  dplyr::filter(GEOID %in% outlier.tracts$id.num) %>%
  dplyr::filter(building.type == "SF") %>%
  dplyr::mutate_if(is.character, as.factor) %>%
  summary()
```

The number of floors are very large.

```{r cmpAreaUsetypeTractMap, fig.show="hold", out.width="100%", message=FALSE, eval=TRUE}
for (i in seq_along(usetypes)) {
  p4 <- total.ann.tract.use.cmp %>%
    dplyr::filter(usetype == usetypes[[i]]) %>%
    dplyr::inner_join(tract.ca, by=c("id.num"="GEOID")) %>%
    tibble::as_tibble() %>%
    sf::st_as_sf() %>%
    ## ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
    tm_shape() +
    tm_polygons("m2", n=5, style="quantile", palette="Purples") +
    tm_facets(by="data.source") +
    tm_layout(main.title = sprintf("Building size for %s (m2)", labels[[i]]),
              main.title.size = 1.2,
              legend.position=c("left", "bottom"), legend.outside=FALSE)
  print(p4)
}
```

## Compare the census tract level kwh usage between EnergyAtlas and simulation for single and multi-family buildings, restricted to the census tracts with data in both data sources

```{r tractUsageCmp, fig.show="hold", out.width="50%", message=FALSE}
upper.lims = c(NA, NA)
for (i in seq_along(usetypes)) {
  p1 <- to.plot.total.ann.use.tract.cmp %>%
    dplyr::filter(variable == "usage", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, `Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ## ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                            after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("%s electricity + gas usage (kWh)", labels[[i]])) +
    ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::theme()
  print(p1)
  p2 <- total.ann.tract.use.cmp %>%
    dplyr::filter(!stringr::str_detect(data.source, "Xuan")) %>%
    dplyr::mutate(kwh.per.m2 = usage / m2) %>%
    dplyr::filter(usetype == usetypes[[i]]) %>%
    dplyr::inner_join(tract.ca.2229, by=c("id.num"="GEOID")) %>%
    tibble::as_tibble() %>%
    sf::st_as_sf() %>%
    tm_shape() +
    tm_polygons("usage", n=5, style="quantile") +
    tm_facets(by="data.source") +
    tm_layout(main.title = sprintf("%s electricity + gas usage (kWh)", labels[[i]]),
              main.title.size = 1.2,
              legend.position=c("left", "bottom"), legend.outside=FALSE)
  print(p2)
}
```

```{r getXuanSimResults, message=FALSE, eval=FALSE}
## fixme: compare with Xuan's simulation results
df.xuan.sim.lsf.files <- list.files("../xuan_sim_output_from_server/", pattern="*LSF-out.csv")

df.xuan.sim.lsf.files %>% head()

lapply(df.xuan.sim.lsf.files, function(f) {

  f = df.xuan.sim.lsf.files[[1]]

  readr::read_csv(sprintf("../xuan_sim_output_from_server/%s", f)) %>%
    dplyr::select(`Date/Time`, `Electricity:Facility [J](Hourly)`, `NaturalGas:Facility [J](Hourly)`) %>%
    tidyr::separate(`Date/Time`, into=c("month", "day"), sep="/") %>%
    tidyr::separate(`day`, into=c("day", "suf"), sep="\\s+") %>%
    dplyr::group_by(month, day) %>%
    dplyr::summarise_if(is.numeric, sum) %>%
    dplyr::ungroup() %>%
    dplyr::mutate_at(vars(month, day), as.numeric) %>%
    dplyr::arrange(month, day) %>%
    tail() %>%
    {.}

})
```

## Compare the neighborhood level total building size between EnergyAtlas and simulation for single and multi-family buildings, restricted to the neighborhodds with data in both data sources

```{r cmpAreaUsetypeNb, fig.show="hold", out.width="50%", message=FALSE, eval=TRUE}
la.nb.geo <- sf::st_read("../energyAtlas/Neighborhood/neighborhoods/neighborhoods.shp")
wrf.grid.with.building <- sf::st_read("../grid_with_building.geojson")

usetypes = c("SingleFamily", "MultiFamily")
labels = c("Single-Family", "Multi-Family")

## upper.lims = c(1.5e7, 8e6, 2.5e5, 5e6)
upper.lims = c(NA, NA)
for (i in seq_along(usetypes)) {
  p1 <- to.plot.total.ann.use.cmp %>%
    dplyr::filter(variable == "m2", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, `Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ## ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                            after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("%s total building area (m2)", labels[[i]])) +
    ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::theme()
  print(p1)
  p2 <- total.ann.nb.use.cmp %>%
    dplyr::filter(usetype == usetypes[[i]]) %>%
    dplyr::inner_join(la.nb.geo, by=c("id.num"="neighborho")) %>%
    tibble::as_tibble() %>%
    sf::st_as_sf() %>%
    ## ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
    tm_shape() +
    tm_polygons("m2", n=5, style="quantile", palette="Purples") +
    tm_facets(by="data.source") +
    tm_layout(main.title = sprintf("Building size for %s (m2)", labels[[i]]),
              main.title.size = 1.2,
              legend.position=c("left", "bottom"), legend.outside=FALSE)
  print(p2)
}
```

## Compare the neighborhood level kwh usage between EnergyAtlas and simulation for single and multi-family buildings, restricted to the neighborhodds with data in both data sources

```{r visByUsetype2, fig.show="hold", out.width="50%", message=FALSE}
upper.lims = c(NA, NA)
for (i in seq_along(usetypes)) {
  p1 <- to.plot.total.ann.use.cmp %>%
    dplyr::filter(variable == "usage", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, `Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ## ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                            after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("%s electricity + gas usage (kWh)", labels[[i]])) +
    ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::theme()
  print(p1)
  p2 <- total.ann.nb.use.cmp %>%
    dplyr::group_by(id.num, usetype) %>%
    dplyr::filter(n() == 2) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(kwh.per.m2 = usage / m2) %>%
    dplyr::filter(usetype == usetypes[[i]]) %>%
    dplyr::inner_join(la.nb.geo, by=c("id.num"="neighborho")) %>%
    tibble::as_tibble() %>%
    sf::st_as_sf() %>%
    tm_shape() +
    tm_polygons("usage", n=5, style="quantile") +
    tm_facets(by="data.source") +
    tm_layout(main.title = sprintf("%s electricity + gas usage (kWh)", labels[[i]]),
              main.title.size = 1.2,
              legend.position=c("left", "bottom"), legend.outside=FALSE)
  print(p2)
}
```
