---
title: "Verify With Neighborhood"
author: "Yujie Xu"
date: "4/15/2022"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "~/Dropbox/workLBNL/EESA/code/im3-wrf/rmd")
```
Verify with Energy Atlas: monthly consumption at neighborhood level in 2016.

## Reading data

Neighborhood geometry shapefile is from an email from Eric Daniel Fournier.

```{r read_neighborhood_geo, message=FALSE}
library("dplyr")
library("ggplot2")
library("sf")
library("tmap")

firstRun = FALSE

la.nb.geo <- sf::st_read("../energyAtlas/Neighborhood/neighborhoods/neighborhoods.shp")

la.nb.geo %>%
  ggplot2::ggplot() +
  ggplot2::geom_sf(size = 0.2) +
  ggplot2::ggtitle("Neighborhood geometry") +
  ggplot2::theme()

```

The following is a preview of the neighborhood data.

```{r nb_data_head, message=FALSE}
la.nb.geo %>%
  head()
```

The following is a summary of the neighborhood shapefile data. The "neighborho" column is used in matching the neighborhood geometry with Energy Atlas neighborhood level energy.

```{r nb_data_summary, message=FALSE}
la.nb.no.geom <- la.nb.geo
sf::st_geometry(la.nb.no.geom) <- NULL

la.nb.no.geom %>%
  tibble::as_tibble() %>%
  dplyr::mutate(neighborho = as.factor(neighborho)) %>%
  dplyr::mutate_if(is.character, as.factor) %>%
  summary()
```

```{r getBuildingInfo, message=FALSE}
if (firstRun) {
  df.grid = readr::read_csv("../compiled_cell_building.csv")
  df.area <- readr::read_csv("../LA_building_footprint_m2.csv")
  df.vin.type.idf <- readr::read_csv("../type_vintage_to_idf_mapping.csv") %>%
    dplyr::select(-building.count) %>%
    {.}
  df.area.prototype = readr::read_csv("../prototype_bldg_area.csv") %>%
    dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
    dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
    dplyr::select(-idf.name) %>%
    {.}
  building.info <- df.grid %>%
    dplyr::inner_join(df.area, by="OBJECTID") %>%
    dplyr::mutate(building.area.m2 = SQFTmain * 0.0929) %>%
    dplyr::select(id, OBJECTID, vintage, building.type, building.area.m2, FootprintArea.m2) %>%
    dplyr::rename(epw.id=id) %>%
    dplyr::inner_join(df.vin.type.idf, by=c("building.type", "vintage")) %>%
    dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
    dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
    dplyr::left_join(df.area.prototype, by="idf.kw") %>%
    {.}
  building.info %>%
    readr::write_csv("../building_info.csv")
} else {
  building.info <- readr::read_csv("../building_info.csv")
}
```

Following is the neighborhood geometry restricted within the boundary of LA county. This is the area we'll analyze.

```{r cmp_la_boundary, message=FALSE}
sf::sf_use_s2(TRUE)
la.boundary <- sf::st_read("../domain/la-county-boundary.geojson")
la.boundary.valid <- sf::st_make_valid(la.boundary)

la.nb.geo.4326 <- sf::st_transform(la.nb.geo, crs=4326)
la.nb.geo.4326.valid = sf::st_make_valid(la.nb.geo.4326)

la.nb.geo.4326.valid %>%
  sf::st_join(la.boundary.valid, join=sf::st_intersects) %>%
  dplyr::filter(!is.na(CITY)) %>%
  ggplot2::ggplot() +
  ggplot2::geom_sf() +
  ggplot2::geom_sf(data=la.boundary, colour = "red",fill=NA) +
  ggplot2::theme()
```

Join building to neighborhood by first computing the building centroids, and check which neighborhood polygon contains the centroid.
```{r join_bd_nb, message=FALSE}
if (firstRun) {
  df.building <- sf::st_read("~/Dropbox/workLBNL/CityBES/LA/data-raw/compiled_LA_building.geojson")

  df.building.valid <- sf::st_make_valid(df.building)

  df.building.centroid <- sf::st_centroid(df.building.valid)

  df.building.nb <- sf::st_join(df.building.centroid, la.nb.geo.4326.valid, join = sf::st_within) %>%
    {.}

  df.building.nb.no.geom <- df.building.nb

  sf::st_geometry(df.building.nb.no.geom) <- NULL

  df.building.nb.no.geom <- df.building.nb.no.geom %>%
    tibble::as_tibble()

  building.nb.match <- df.building.nb.no.geom %>%
    distinct(OBJECTID, neighborho) %>%
    {.}

  building.nb.match %>%
    readr::write_csv("../building_id_to_neighborhood.csv")
} else {
  building.nb.match = readr::read_csv("../building_id_to_neighborhood.csv")
}

```

The following is a preview of the matching result data frame

```{r previewMatchBuildingNb, message=FALSE}
building.nb.match %>%
  head() %>%
  knitr::kable()
```

The following is a summary of the matching
```{r summaryMatchBuildingNb, message=FALSE}
building.nb.match %>%
  dplyr::group_by(neighborho) %>%
  dplyr::summarise(num.building = n()) %>%
  dplyr::ungroup() %>%
  dplyr::summarise_at(vars(num.building),
                      tibble::lst(min, "Q1"=~quantile(., probs=0.25), median, mean, "Q3"=~quantile(., probs=0.75), max)) %>%
  dplyr::ungroup() %>%
  knitr::kable(caption = "Summary stats of the number of buildings matched to a neighborhood")
  ## ggplot2::ggplot(ggplot2::aes(x = num.building)) +
  ## ggplot2::ggtitle("The distribution of number of buildings matched to each neighborhood") +
  ## ggplot2::geom_histogram()
```

Read neighborhood level annual energy data, usage_bld_kwh.csv, downloaded from
the Energy Atlas website,
https://ucla.app.box.com/s/z2i515cc2lgn3t6rpwe1ymcqygr4y5a0. Different from the
Dropbox data, the new data has "masked" and NA’s in the usage column instead of
the -7777, -8888, -9999 code. The "all" category is also removed in the new data
set. "id" column is renamed to "geo_id". The following is a preview of the usage_bld_kwh.csv

```{r readEnergyAtlas, message=FALSE}
la.energy <- readr::read_csv("../energyAtlas/usage_bld_kwh.csv")

la.energy %>%
  head() %>%
  knitr::kable(caption = "Preview of usage_bld_kwh.csv")
```

Join Energy Atlas energy data with neighborhood geometry
* First split the "geo_id" column by the "_"
* Filtering out the id's at neighborhood level (prefix of "geo_id" == "neighborhoods")
* Join the energy and shapefile data with the numeric suffix of "geo_id" and the "neighborho" column in the shapefile

```{r readEnergyAtlas2, message=FALSE}
## neighborhood with building
nb.with.bd <- building.nb.match %>%
  tibble::as_tibble() %>%
  dplyr::filter(!is.na(neighborho)) %>%
  dplyr::inner_join(building.info, by="OBJECTID") %>%
  dplyr::distinct(neighborho) %>%
  {.}

la.energy.nb <- la.energy %>%
  tidyr::separate(geo_id, c("id.type", "id.num")) %>%
  dplyr::filter(id.type == "neighborhoods") %>%
  dplyr::mutate(id.num = as.numeric(id.num)) %>%
  {.}
```

Filter the data by four steps. The following table shows the number of
neighborhoods and records left after each step. The last step is meant to
calculate the total usage for a neighborhood. As is shown here, the building types in EnergyAtlas overlaps. In order to compute the total of a neighborhood, we need to keep only the non-overlapping usetyeps. The definition of each use type are as following according to https://energyatlas.ucla.edu/methods

```{r filteringNbData, message=FALSE}
df.usetype.def <- readr::read_csv("../energyAtlas/usetype_def.csv")

## restrict to grids with buildings
la.energy.nb.withinLA <- la.energy.nb %>%
  dplyr::inner_join(nb.with.bd, by=c("id.num"="neighborho")) %>%
  {.}

## remove masked
la.energy.nb.not.masked <- la.energy.nb.withinLA %>%
  dplyr::filter(usage != "masked") %>%
  dplyr::mutate(usage = as.numeric(usage)) %>%
  {.}

## sqft > 0
la.energy.nb.positive.size <- la.energy.nb.not.masked %>%
  dplyr::filter(sqft > 0) %>%
  {.}

la.energy.nb.positive.size %>%
  dplyr::distinct(usetype) %>%
  dplyr::left_join(df.usetype.def, by="usetype") %>%
  knitr::kable(caption="Usetypes in the EnergyAtlas data after filtering by size > 0")

## not in agriculture or other usetype
la.energy.nb.filter <- la.energy.nb.positive.size %>%
  dplyr::filter(!(usetype %in% c("agriculture", "other"))) %>%
  {.}

la.energy.nb.within.fourtypes <- la.energy.nb.filter %>%
  dplyr::filter(usetype %in% c("res_total", "commercial", "industrial", "institutional")) %>%
  {.}

dfs = list(la.energy.nb, la.energy.nb.withinLA, la.energy.nb.not.masked,
           la.energy.nb.positive.size, la.energy.nb.filter,
           la.energy.nb.within.fourtypes)
number.of.nbs <- sapply(dfs, function(df) {
  df %>%
    dplyr::distinct(id.num) %>%
    nrow()
})
number.of.records <- sapply(dfs, function(df) {
  df %>%
    nrow()
})

filtering.steps <- c("Original data",
                     "Restrict to within LA county",
                     "Remove masked data",
                     "Keep records with positive sqft",
                     "Remove agriculture and \"other\" usetype",
                     "Restrict to the major usetypes")

tibble::tibble(`Filtering Steps`=filtering.steps,
               `Number of Neighborhoods`=number.of.nbs,
               `Number of Records`=number.of.records) %>%
  knitr::kable(caption = "Filtering steps and the number of neighborhoods and records remaining")
```

```{r EnergyAtlasAggregateToNb, message=FALSE}
la.energy.nb.total <- la.energy.nb.within.fourtypes %>%
  dplyr::group_by(id.num) %>%
  dplyr::summarise_if(is.numeric, sum) %>%
  dplyr::ungroup() %>%
  ## here sqft is total building area
  dplyr::mutate(data.source = "Energy Atlas 2016",
                m2 = sqft * 0.092903) %>%
  dplyr::select(id.num, usage, m2, data.source) %>%
  {.}
```

Following is a preview of the aggregated Energy Atlas data by neighborhood and by neighborhood and usetype

```{r viewEnergyAtlasDataTotal, message=FALSE}
## fixme: should here keep all overlapping types as well?
la.energy.nb.use.total <- la.energy.nb.within.fourtypes %>%
  dplyr::select(id.num, usetype, sqft, usage) %>%
  dplyr::mutate(data.source = "Energy Atlas 2016",
                m2 = sqft * 0.092903) %>%
  dplyr::select(id.num, usetype, usage, m2, data.source) %>%
  {.}

la.energy.nb.total %>%
  head() %>%
  knitr::kable()

la.energy.nb.use.total %>%
  head() %>%
  knitr::kable()
```

Simulation results are saved in a csv file: annual_sim_result_by_idf_epw.csv 

First aggregate simulation results to annual total, and convert the consumption
from J to kwh.

```{r annual_energy, message=FALSE}

if (firstRun) {
  result.ann <- readr::read_csv("../annual_sim_result_by_idf_epw.csv")
  annual.total.result <- result.ann %>%
    dplyr::group_by(idf.kw, epw.id) %>%
    dplyr::summarise_if(is.numeric, sum) %>%
    dplyr::ungroup() %>%
    dplyr::select(idf.kw, epw.id, energy.overall) %>%
    dplyr::mutate(epw.id = as.numeric(epw.id)) %>%
    {.}
  annual.total.result %>%
    readr::write_csv("../annual_total_result.csv")
} else {
  annual.total.result <- readr::read_csv("../annual_total_result.csv")
}

sim.ann.nb.join <- building.nb.match %>%
  tibble::as_tibble() %>%
  dplyr::filter(!is.na(neighborho)) %>%
  dplyr::inner_join(building.info, by="OBJECTID") %>%
  dplyr::mutate(idf.kw = gsub(".idf", "", idf.name, fixed=TRUE)) %>%
  dplyr::mutate(idf.kw = gsub(".", "_", idf.kw, fixed=TRUE)) %>%
  dplyr::inner_join(annual.total.result, by=c("idf.kw", "epw.id")) %>%
  dplyr::mutate(energy.kwh = energy.overall * 1e-9 * 277.778) %>%
  {.}

sim.ann.agg.to.nb <- sim.ann.nb.join %>%
  dplyr::group_by(neighborho) %>%
  summarise_at(vars(energy.kwh, building.area.m2, FootprintArea.m2), sum) %>%
  dplyr::ungroup() %>%
  {.}

```

Then map building types in the simulation data set to the
EnergyAtlas types. Note that nursing homes are matched to residential rather
than institutional. The following table shows the mapping from EnergyPlus models
to EnergyAtlas types

```{r usetypeMap, warning=FALSE, message=FALSE}
idf.kw.to.usetype <- readr::read_csv("../idf_kw_to_EnergyAtlas_usetype.csv")
idf.kw.to.usetype %>%
  tidyr::separate(idf.kw, sep="-", c("simulation", "t2")) %>%
  distinct(simulation, usetype) %>%
  dplyr::rename(EnergyAtlas=usetype) %>%
  select(EnergyAtlas, simulation) %>%
  arrange(EnergyAtlas, simulation) %>%
  knitr::kable(caption="Simulation type to EnergyAtlas type mapping", format="html") %>%
  kableExtra::collapse_rows() %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

```{r mapTypes, message=FALSE}
sim.ann.agg.to.nb.use <- sim.ann.nb.join %>%
  dplyr::inner_join(idf.kw.to.usetype, by="idf.kw") %>%
  dplyr::group_by(neighborho, usetype) %>%
  summarise_at(vars(energy.kwh, building.area.m2, FootprintArea.m2), sum) %>%
  dplyr::ungroup() %>%
  {.}

sim.ann.agg.to.nb.geo <- sim.ann.agg.to.nb %>%
  dplyr::inner_join(la.nb.geo, by="neighborho") %>%
  sf::st_as_sf() %>%
  {.}

## sim.ann.agg.to.nb.geo %>%
##   sf::st_write("../geo_output/sim_ann_agg_to_neighborhood.geojson")
```

Following is a preview of the simulation results aggregated to neighborhood level

```{r previewSimResult, message = FALSE}
sim.ann.agg.to.nb %>%
  head() %>%
  knitr::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

sim.ann.agg.to.nb.use %>%
  head() %>%
  knitr::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

```{r joinSimEnergyAtlas, message = FALSE}

total.ann.cmp <- sim.ann.agg.to.nb %>%
  dplyr::select(neighborho, energy.kwh, building.area.m2) %>%
  dplyr::rename(id.num=neighborho, usage=energy.kwh, m2=building.area.m2) %>%
  dplyr::mutate(data.source = "Simulation 2018") %>%
  dplyr::bind_rows(la.energy.nb.total) %>%
  {.}

total.ann.nb.use.cmp <- sim.ann.agg.to.nb.use %>%
  dplyr::select(neighborho, usetype, energy.kwh, building.area.m2) %>%
  dplyr::rename(id.num=neighborho, usage=energy.kwh, m2=building.area.m2) %>%
  dplyr::mutate(data.source = "Simulation 2018") %>%
  dplyr::bind_rows(la.energy.nb.use.total) %>%
  {.}

to.plot.total.ann.cmp <- total.ann.cmp %>%
  dplyr::mutate(kwh.per.m2 = usage / m2) %>%
  dplyr::group_by(id.num) %>%
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup() %>%
  tidyr::gather(variable, value, c(usage, m2, kwh.per.m2)) %>%
  tidyr::spread(data.source, value) %>%
  {.}

to.plot.total.ann.use.cmp <- total.ann.nb.use.cmp %>%
  dplyr::mutate(kwh.per.m2 = usage / m2) %>%
  dplyr::group_by(id.num, usetype) %>%
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup() %>%
  tidyr::gather(variable, value, c(usage, m2, kwh.per.m2)) %>%
  tidyr::spread(data.source, value) %>%
  {.}

to.plot.total.ann.use.cmp %>%
  readr::write_csv("to_plot_total_ann_use_cmp.csv")
```

## Visualize neighborhood level simulation data
```{r vis, message=FALSE, fig.show="hold", out.width="50%", message=FALSE}
wrf.grid.with.building <- sf::st_read("../grid_with_building.geojson")
sim.ann.agg.to.nb.geo %>%
  ggplot2::ggplot(ggplot2::aes(fill = energy.kwh)) +
  ggplot2::geom_sf(size = 0.2) +
  ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
  ggplot2::scale_fill_distiller(palette = "YlOrBr", direction = 1) +
  ggplot2::ggtitle("Neighborhood annual electricity + gas consumption (kWh)") +
  ggplot2::theme(axis.ticks.x = ggplot2::element_blank(),
                 axis.ticks.y = ggplot2::element_blank(),
                 axis.text.x = ggplot2::element_blank(),
                 axis.text.y = ggplot2::element_blank())

sim.ann.agg.to.nb.geo %>%
  ggplot2::ggplot(ggplot2::aes(fill = building.area.m2)) +
  ggplot2::geom_sf(size = 0.2) +
  ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
  ggplot2::scale_fill_distiller(palette = "Purples", direction = 1) +
  ggplot2::ggtitle("total building area (m2)") +
  ggplot2::theme(axis.ticks.x = ggplot2::element_blank(),
                 axis.ticks.y = ggplot2::element_blank(),
                 axis.text.x = ggplot2::element_blank(),
                 axis.text.y = ggplot2::element_blank())

sim.ann.agg.to.nb.geo %>%
  dplyr::mutate(W.per.m2 = energy.kwh * 1000 / building.area.m2) %>%
  ggplot2::ggplot(ggplot2::aes(fill = W.per.m2)) +
  ggplot2::geom_sf(size = 0.2) +
  ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
  ggplot2::scale_fill_distiller(palette = "YlOrBr", direction = 1) +
  ggplot2::ggtitle("Building size normalized annual electricity + gas usage (W/m2)") +
  ggplot2::theme(axis.ticks.x = ggplot2::element_blank(),
                 axis.ticks.y = ggplot2::element_blank(),
                 axis.text.x = ggplot2::element_blank(),
                 axis.text.y = ggplot2::element_blank())

sim.ann.agg.to.nb.geo %>%
  dplyr::mutate(W.per.m2 = energy.kwh * 1000 / FootprintArea.m2) %>%
  ggplot2::ggplot(ggplot2::aes(fill = W.per.m2)) +
  ggplot2::geom_sf(size = 0.2) +
  ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
  ggplot2::scale_fill_distiller(palette = "YlOrBr", direction = 1) +
  ggplot2::ggtitle("Building footprint normalized annual electricity + gas usage (W/m2)") +
  ggplot2::theme(axis.ticks.x = ggplot2::element_blank(),
                 axis.ticks.y = ggplot2::element_blank(),
                 axis.text.x = ggplot2::element_blank(),
                 axis.text.y = ggplot2::element_blank())
```

## Compare Energy Atlas and Simulation results

For most neighborhoods, the total building area recorded in Energy Atlas is larger than the area recorded in the simulation data set (building characteristics source data is from "Assessor_Parcels_Data_-_2019.csv" joined to the building geometry from LARIAC6_LA_County.geojson)

```{r cmpArea, message=FALSE, fig.show="hold", out.width="50%"}
to.plot.total.ann.cmp %>%
  dplyr::filter(variable == "m2") %>%
  ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, `Energy Atlas 2016`)) +
  ggplot2::coord_cartesian(xlim=c(0, 2.1e7), ylim=c(0, 2.1e7)) +
  ggplot2::geom_point(size = 0.2) +
  ggplot2::geom_smooth(method="lm", size = 0.5) +
  ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  ggplot2::ggtitle("Total building area (m2)") +
  ggplot2::theme()

total.ann.cmp %>%
  dplyr::mutate(kwh.per.m2 = usage / m2) %>%
  dplyr::group_by(id.num) %>%
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup() %>%
  ## dplyr::mutate(kwh.per.m2.bin = case_when(kwh.per.m2 < 70 ~ "<70",
  ##                                          kwh.per.m2 < 100 ~ "70-100",
  ##                                          kwh.per.m2 < 150 ~ "70-150",
  ##                                          TRUE ~ ">= 150")) %>%
  dplyr::inner_join(la.nb.geo, by=c("id.num"="neighborho")) %>%
  tibble::as_tibble() %>%
  sf::st_as_sf() %>%
  ggplot2::ggplot(ggplot2::aes(fill = m2)) +
  ggplot2::geom_sf(size = 0.2) +
  ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
  ggplot2::scale_fill_distiller(palette = "Purples", direction = 1) +
  ## ggplot2::scale_fill_brewer(palette = "Purples", direction = 1) +
  ggplot2::ggtitle("Building size (m2)") +
  ggplot2::facet_wrap(.~data.source) +
  ggplot2::theme(axis.ticks.x = ggplot2::element_blank(),
                 axis.ticks.y = ggplot2::element_blank(),
                 axis.text.x = ggplot2::element_blank(),
                 axis.text.y = ggplot2::element_blank())

```

The following compares the building total sqft of the four major usetypes.

For most neighborhoods, the total building area recorded in Energy Atlas for each of the four major usetypes is larger than the area recorded in the simulation data set.

The following plots the difference in the percentage of each four usetypes in a neighborhood. We can see that simulation data sets have higher percentage of residential and industrial types and lower ratio of commercial buildings in most neighborhoods, compared against Energy Atlas data.

```{r compareRatioOfType, message=FALSE}
area.ratio.of.usetypes <- to.plot.total.ann.use.cmp %>%
  dplyr::filter(variable == "m2") %>%
  dplyr::select(-variable) %>%
  tidyr::gather(data.source, m2, `Energy Atlas 2016`:`Simulation 2018`) %>%
  dplyr::group_by(id.num, data.source) %>%
  dplyr::mutate(total.m2 = sum(m2)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(ratio = m2 / total.m2) %>%
  {.}

area.ratio.of.usetypes %>%
  readr::write_csv("../area_ratio_of_usetypes.csv")

area.ratio.of.usetypes %>%
  dplyr::select(-m2, -total.m2) %>%
  tidyr::spread(data.source, ratio) %>%
  dplyr::mutate(ratio.diff = `Simulation 2018` - `Energy Atlas 2016`) %>%
  ggplot2::ggplot(ggplot2::aes(x = usetype, y=ratio.diff)) +
  ggplot2::geom_violin() +
  ggplot2::geom_boxplot(width = 0.1, outlier.shape = NA) +
  ggplot2::geom_jitter(size = 0.1) +
  ggplot2::coord_flip() +
  ggplot2::ggtitle("Compare (simulation usetype ratio - Energy Atlas usetype ratio) difference for the four major types") +
  ggplot2::theme()
```

```{r cmpAreaUsetype, fig.show="hold", out.width="50%", message=FALSE, eval=TRUE}
usetypes = c("res_total", "commercial", "institutional", "industrial")
labels = c("residential", "commercial", "institutional", "industrial")

## upper.lims = c(1.5e7, 8e6, 2.5e5, 5e6)
upper.lims = c(NA, NA, NA, NA)
for (i in seq_along(usetypes)) {
  p1 <- to.plot.total.ann.use.cmp %>%
    dplyr::filter(variable == "m2", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, `Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("%s total building area (m2)", labels[[i]])) +
    ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::theme()
  print(p1)
  p2 <- total.ann.nb.use.cmp %>%
    dplyr::filter(usetype == usetypes[[i]]) %>%
    dplyr::inner_join(la.nb.geo, by=c("id.num"="neighborho")) %>%
    tibble::as_tibble() %>%
    sf::st_as_sf() %>%
    ggplot2::ggplot(ggplot2::aes(fill = m2)) +
    ggplot2::geom_sf(size = 0.2) +
    ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
    ggplot2::scale_fill_distiller(palette = "Purples", direction = 1) +
    ## ggplot2::scale_fill_brewer(palette = "Purples", direction = 1) +
    ggplot2::ggtitle(sprintf("Building size for %s (m2)", labels[[i]])) +
    ggplot2::facet_wrap(.~data.source) +
    ggplot2::theme(axis.ticks.x = ggplot2::element_blank(),
                   axis.ticks.y = ggplot2::element_blank(),
                   axis.text.x = ggplot2::element_blank(),
                   axis.text.y = ggplot2::element_blank())
  print(p2)
}

```

## Compare the kwh/m2 and kwh between the two data set

The following shows the total energy usage and usage per total area comparison.

```{r visOfcmp, fig.show="hold", out.width="50%", message=FALSE}
to.plot.total.ann.cmp %>%
  dplyr::filter(variable == "usage") %>%
  ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, `Energy Atlas 2016`)) +
  ggplot2::coord_cartesian(xlim=c(0, 3.42e9), ylim=c(0, 3.42e9)) +
  ggplot2::geom_point(size = 0.2) +
  ggplot2::geom_smooth(method="lm", size = 0.5) +
  ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  ggplot2::ggtitle("Electricity + gas usage (kWh)") +
  ggplot2::theme()

total.ann.cmp %>%
  dplyr::mutate(kwh.per.m2 = usage / m2) %>%
  dplyr::group_by(id.num) %>%
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup() %>%
  dplyr::inner_join(la.nb.geo, by=c("id.num"="neighborho")) %>%
  tibble::as_tibble() %>%
  sf::st_as_sf() %>%
  tm_shape() +
  tm_polygons("usage", n=5, style="quantile") +
  tm_facets(by="data.source") +
  tm_layout(main.title = "Electricity + gas usage (kWh)",
            legend.position=c("left", "bottom"), legend.outside=FALSE)

to.plot.total.ann.cmp %>%
  dplyr::filter(variable == "kwh.per.m2") %>%
  ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, `Energy Atlas 2016`)) +
  ggplot2::coord_cartesian(xlim=c(0, 700), ylim=c(0, 700)) +
  ## ggplot2::coord_cartesian(xlim=c(0, 2500), ylim=c(0, 2500)) +
  ggplot2::geom_point(size = 0.2) +
  ggplot2::geom_smooth(method="lm", size = 0.5) +
  ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  ggplot2::ggtitle("Electricity + gas usage per total building area \n(kWh/m2)") +
  ggplot2::theme()

total.ann.cmp %>%
  dplyr::mutate(kwh.per.m2 = usage / m2) %>%
  dplyr::group_by(id.num) %>%
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup() %>%
  dplyr::inner_join(la.nb.geo, by=c("id.num"="neighborho")) %>%
  tibble::as_tibble() %>%
  sf::st_as_sf() %>%
  tm_shape() +
  tm_polygons("kwh.per.m2", n=5, style="quantile") +
  tm_facets(by="data.source") +
  tm_layout(main.title = "Building size normalized annual electricity + gas usage (kWh/m2)",
            main.title.size = 1.2,
            legend.position=c("left", "bottom"), legend.outside=FALSE)

```

## Compare the kwh/m2 usage between EnergyAtlas and simulation by different use types, restricted to the neighborhodds with data in both data sources

```{r visByUsetype, fig.show="hold", out.width="50%", message=FALSE}
usetypes = c("res_total", "commercial", "institutional", "industrial")
labels = c("residential", "commercial", "institutional", "industrial")
upper.lims = c(NA, 1500, 1800, 3500)
for (i in seq_along(usetypes)) {
  p1 <- to.plot.total.ann.use.cmp %>%
    dplyr::filter(variable == "kwh.per.m2", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, `Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("%s electricity + gas usage \nper total building area (kWh/m2)", labels[[i]])) +
    ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::theme()
  print(p1)
  p2 <- total.ann.nb.use.cmp %>%
    dplyr::group_by(id.num, usetype) %>%
    dplyr::filter(n() == 2) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(kwh.per.m2 = usage / m2) %>%
    dplyr::filter(usetype == usetypes[[i]]) %>%
    dplyr::inner_join(la.nb.geo, by=c("id.num"="neighborho")) %>%
    tibble::as_tibble() %>%
    sf::st_as_sf() %>%
    tm_shape() +
    tm_polygons("kwh.per.m2", n=5, style="quantile") +
    tm_facets(by="data.source") +
    tm_layout(main.title = sprintf("%s electricity + gas usage per total building area (kWh/m2)", labels[[i]]),
              main.title.size = 1.2,
              legend.position=c("left", "bottom"), legend.outside=FALSE)
  print(p2)
}
```

## Compare the kwh usage between EnergyAtlas and simulation by different use types, restricted to the neighborhodds with data in both data sources

```{r visByUsetype2, fig.show="hold", out.width="50%", message=FALSE}
## upper.lims = c(1e9, 1.5e9, 1.25e8, 2e9)
upper.lims = c(NA, NA, NA, NA)
for (i in seq_along(usetypes)) {
  p1 <- to.plot.total.ann.use.cmp %>%
    dplyr::filter(variable == "usage", usetype == usetypes[[i]]) %>%
    ggplot2::ggplot(ggplot2::aes(x=`Simulation 2018`, `Energy Atlas 2016`)) +
    ggplot2::geom_point(size = 0.2) +
    ggplot2::geom_smooth(method="lm", size = 0.5) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(sprintf("%s electricity + gas usage (kWh)", labels[[i]])) +
    ggplot2::coord_cartesian(xlim = c(0, upper.lims[[i]]), ylim = c(0, upper.lims[[i]])) +
    ggplot2::theme()
  print(p1)
  p2 <- total.ann.nb.use.cmp %>%
    dplyr::group_by(id.num, usetype) %>%
    dplyr::filter(n() == 2) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(kwh.per.m2 = usage / m2) %>%
    dplyr::filter(usetype == usetypes[[i]]) %>%
    dplyr::inner_join(la.nb.geo, by=c("id.num"="neighborho")) %>%
    tibble::as_tibble() %>%
    sf::st_as_sf() %>%
    tm_shape() +
    tm_polygons("usage", n=5, style="quantile") +
    tm_facets(by="data.source") +
    tm_layout(main.title = sprintf("%s electricity + gas usage (kWh)", labels[[i]]),
              main.title.size = 1.2,
              legend.position=c("left", "bottom"), legend.outside=FALSE)
  print(p2)
}
```

## Compare the Distribution

```{r visOverall, fig.show="hold", out.width="80%", message=FALSE}
## total.ann.cmp %>%
##   dplyr::mutate(kwh.per.m2 = usage / m2) %>%
##   dplyr::group_by(id.num) %>%
##   dplyr::filter(n() == 2) %>%
##   dplyr::ungroup() %>%
##   dplyr::inner_join(la.nb.geo, by=c("id.num"="neighborho")) %>%
##   tibble::as_tibble() %>%
##   sf::st_as_sf() %>%
##   ggplot2::ggplot(ggplot2::aes(fill = kwh.per.m2)) +
##   ggplot2::geom_sf(size = 0.2) +
##   ggplot2::geom_sf(data=wrf.grid.with.building, fill=NA, size=0.1) +
##   ggplot2::scale_fill_distiller(palette = "YlOrBr", direction = 1) +
##   ggplot2::ggtitle("Building size normalized annual electricity + gas usage (W/m2)") +
##   ggplot2::facet_wrap(.~data.source) +
##   ggplot2::theme(axis.ticks.x = ggplot2::element_blank(),
##                  axis.ticks.y = ggplot2::element_blank(),
##                  axis.text.x = ggplot2::element_blank(),
##                  axis.text.y = ggplot2::element_blank())

## density
total.ann.cmp %>%
  dplyr::mutate(kwh.per.m2 = usage / m2) %>%
  dplyr::group_by(id.num) %>%
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup() %>%
  ggplot2::ggplot(ggplot2::aes(x=kwh.per.m2, fill=data.source)) +
  ggplot2::geom_histogram(alpha=0.5, binwidth=10) +
  ggplot2::theme()

## voilin
total.ann.cmp %>%
  dplyr::mutate(kwh.per.m2 = usage / m2) %>%
  dplyr::group_by(id.num) %>%
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup() %>%
  ggplot2::ggplot(ggplot2::aes(x=data.source, y=kwh.per.m2)) +
  ggplot2::ggtitle("Building size normalized \nannual electricity + gas usage (kWh/m2)") +
  ggplot2::geom_violin() +
  ggplot2::geom_boxplot(width=0.05, outlier.shape = NA) +
  ggplot2::theme()
```
